---
title: "Spaces"
author: "Analytics Guild"
date: "01/01/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Setup

Loading libraries and data.

```{r, include=FALSE}
# load library ----
library(tidyverse)

# load data ----
new_member <- read_csv("./discord/raw_data/guild-joins-by-source_010122.csv")
total_member <- read_csv("./discord/raw_data/guild-total-membership_010122.csv")
first_activation <- read_csv("./discord/raw_data/guild-activation_010122.csv")
next_retention <- read_csv("./discord/raw_data/guild-retention_010122.csv")
visit_comm <- read_csv("./discord/raw_data/guild-communicators_010122.csv")
msg_avg <- read_csv("./discord/raw_data/guild-message-activity_010122.csv")
voice_act <- read_csv("./discord/raw_data/guild-voice-activity_010122.csv")

# snapshot data
snapshot_votes <- read_csv("./snapshot/raw_data/snapshot_votes_s2_010122.csv")
```


## New Members: S1 and S2

Showing organic grow

```{r, echo=FALSE}
# JOIN Discord Data S1 and S2 ----

new_member_s2 <- read_csv("../s2_data_activity/discord/raw_data/new-member-joins-by-source_290921.csv")
new_member_s3 <- read_csv("./discord/raw_data/guild-joins-by-source_010122.csv")

# combine s1 and s2
all_new_mem <- rbind(new_member_s2, new_member_s3)

# visualize
all_new_mem %>%
    rename(
        vanity = "vanity_joins",
        discovery = "discovery_joins",
        time = "interval_start_timestamp"
    ) %>%
    pivot_longer(cols = discovery:vanity, names_to = "channel", values_to = "count") %>%
    ggplot(aes(x = time, y = count, fill = channel)) +
    geom_bar(position = "stack", stat = "identity") +
    # geom_text(aes(label = count), position = position_stack(vjust = 1.5), color = "white") +
    # vertical line separating season 1 v season 2
    geom_vline(xintercept = as.POSIXct("2021-10-04", origin = "yyyy-mm-dd"), color = 'white', size = 1.5, linetype = 'dotted') +
    theme(
        legend.position = "bottom",
        legend.background = element_rect(fill = "#65737e"),
        legend.text = element_text(color = "white"),
        legend.title = element_text(color = "white"),
        panel.background = element_rect(fill = "#65737e"),
        panel.grid.major = element_line(color = "#65737e"),
        panel.grid.minor = element_line(color = "#65737e"),
        plot.background = element_rect(fill = "#65737e"),
        axis.text.x = element_text(color = "white"),
        axis.text.y = element_text(color = "white"),
        axis.title.x = element_text(color = "white"),
        axis.title.y = element_text(color = "white"),
        title = element_text(color = "white")
    ) +
    scale_fill_manual(values = c("white", "red", "black")) +
    labs(
        title = "How many new members are joining? (Seasons 1 - 2)",
        subtitle = "Where are they coming from?",
        y = "Joins",
        x = "",
        caption = "data: BanklessDAO Discord | visual: @paulapivat, Analytics Guild"
    )
```



# Total Members: S1 and S2

Up and to the right

```{r, echo=FALSE}
# JOIN Total Member Growth S1 and S2 ----

total_member_s2 <- read_csv("../s2_data_activity/discord/raw_data/total-membership-joins_290921.csv")
total_member_s3 <- read_csv("./discord/raw_data/guild-total-membership_010122.csv")

all_total_mem <- rbind(total_member_s2, total_member_s3)

all_total_mem %>%
    rename(
        time = "interval_start_timestamp",
        total = "total_membership"
    ) %>%
    ggplot(aes(x = time)) +
    geom_line(aes(y = total), color = "red", size = 1.5) +
    geom_vline(xintercept = as.POSIXct("2021-10-04", origin = "yyyy-mm-dd"), color = 'white', size = 1.5, linetype = 'dotted') +
    theme(
        panel.background = element_rect(fill = "#65737e"),
        panel.grid.major = element_line(color = "#65737e"),
        panel.grid.minor = element_line(color = "#65737e"),
        plot.background = element_rect(fill = "#65737e"),
        axis.text.x = element_text(color = "white"),
        axis.text.y = element_text(color = "white"),
        axis.title.x = element_text(color = "white"),
        axis.title.y = element_text(color = "white"),
        title = element_text(color = "white")
    ) +
    labs(
        title = "Total membership over time: S1 and S2",
        y = "",
        x = "",
        caption = "data: BanklessDAO Discord | visual: @paulapivat, Analytics Guild"
    )

```


## First Day Activation: S1 and S2

Voice participation went up in Season 2:

```{r, echo=FALSE}
# JOIN Activation S1 and S2 ----

first_activation_s2 <- read_csv("../s2_data_activity/discord/raw_data/first-day-activation_290921.csv")
first_activation_s3 <- read_csv("./discord/raw_data/guild-activation_010122.csv")

total_activation <- rbind(first_activation_s2, first_activation_s3)

total_activation %>%
    rename(
        time = "interval_start_timestamp",
        new = "new_members",
        talked = "pct_communicated",
        visited = "pct_opened_channels"
    ) %>%
    ggplot(aes(x = time)) +
    geom_bar(aes(y = new, color = "New members"), stat = "identity", fill = "black") +
    geom_line(aes(y = talked*15, color = "% talked (voice or text)"), size = 1.5) +
    geom_line(aes(y = visited*15, color = "% visited more than 3 channels"), size = 1.5) +
    geom_line(y = 480, color = "orange", size = 0.2) +
    # vertical line separating season 1 v season 2
    geom_vline(xintercept = as.POSIXct("2021-10-04", origin = "yyyy-mm-dd"), color = 'white', size = 1.5, linetype = 'dotted') +
    scale_y_continuous(
        name = "New Members",
        sec.axis = sec_axis(trans = ~./1500*100, name = "% Activated")
    ) +
    scale_color_manual(values = c("white", "red", "black")) +
    theme(
        legend.position = "bottom",
        legend.background = element_rect(fill = "#65737e"),
        legend.text = element_text(color = "white"),
        legend.title = element_text(color = "white"),
        panel.background = element_rect(fill = "#65737e"),
        panel.grid.major = element_line(color = "#65737e"),
        panel.grid.minor = element_line(color = "#65737e"),
        plot.background = element_rect(fill = "#65737e"),
        axis.text.x = element_text(color = "white"),
        axis.text.y = element_text(color = "white"),
        axis.title.x = element_text(color = "white"),
        axis.title.y = element_text(color = "white"),
        title = element_text(color = "white")
    ) +
    labs(
        title = "How many new members successfully activate on their first day?",
        subtitle = "S1 and S2",
        x = "",
        color = "Legend",
        caption = "data: BanklessDAO Discord | visual: @paulapivat, Analytics Guild"
    )

```


## Total Retention: S1 and S2

Retention has not improved that much, but we have more new members. 

```{r, echo=FALSE}
# JOIN Retention S1 and S2 ----

next_retention_s1 <- read_csv("../s2_data_activity/discord/raw_data/next-week-retention_290921.csv")
next_retention_s2 <- read_csv("./discord/raw_data/guild-retention_010122.csv")

total_retention <- rbind(next_retention_s1, next_retention_s2)

total_retention %>%
    rename(
        time = "interval_start_timestamp",
        new = "new_members",
        retained = "pct_retained"
    ) %>%
    ggplot(aes(x = time)) +
    geom_bar(aes(y = new, color = "New members"), stat = "identity", fill = "black") +
    geom_line(aes(y = retained*15, color = "Week 1 retention (%)"), size = 1.5) +
    geom_line(y = 320, color = "orange", size = 0.2) +
    # vertical line separating season 1 v season 2
    geom_vline(xintercept = as.POSIXct("2021-10-04", origin = "yyyy-mm-dd"), color = 'white', size = 1.5, linetype = 'dotted') +
    scale_y_continuous(
        name = "New Members",
        sec.axis = sec_axis(trans = ~./1500*100, name = "Week 1 retention (%)")
    ) +
    scale_color_manual(values = c("black", "red")) +
    theme(
        legend.position = "bottom",
        legend.background = element_rect(fill = "#65737e"),
        legend.text = element_text(color = "white"),
        legend.title = element_text(color = "white"),
        panel.background = element_rect(fill = "#65737e"),
        panel.grid.major = element_line(color = "#65737e"),
        panel.grid.minor = element_line(color = "#65737e"),
        plot.background = element_rect(fill = "#65737e"),
        axis.text.x = element_text(color = "white"),
        axis.text.y = element_text(color = "white"),
        axis.title.x = element_text(color = "white"),
        axis.title.y = element_text(color = "white"),
        title = element_text(color = "white")
    ) +
    labs(
        title = "How many new members retain the next week?",
        subtitle = "S1 and S2",
        x = "",
        color = "Legend",
        caption = "data: BanklessDAO Discord | visual: @paulapivat, Analytics Guild"
    )
```



## Total Visitor and Communicator: S1 and S2

Still below benchmark, but trending upward slight in season 2:

```{r, echo=FALSE}
# JOIN Visitors and Communicators: S1 and S2 ----

visit_comm_s1 <- read_csv("../s2_data_activity/discord/raw_data/visitors-communicators_290921.csv")
visit_comm_s2 <- read_csv("./discord/raw_data/guild-communicators_010122.csv")

total_visit_comm <- rbind(visit_comm_s1, visit_comm_s2)

total_visit_comm %>%
    rename(
        time = "interval_start_timestamp",
        comm = "pct_communicated"
    ) %>%
    ggplot(aes(x = time)) +
    geom_bar(aes(y = visitors, color = "Visitors"), stat = "identity", fill = "black") +
    geom_line(aes(y = comm*30, color = "% communicators"), size = 1.5) +
    geom_line(y = 1200, color = "orange", size = 0.2) +
    # vertical line separating season 1 v season 2
    geom_vline(xintercept = as.POSIXct("2021-10-04", origin = "yyyy-mm-dd"), color = 'white', size = 1.5, linetype = 'dotted') +
    scale_y_continuous(
        name = "Visitors",
        sec.axis = sec_axis(trans = ~./3000*100, name = "% Communicators")
    ) +
    scale_color_manual(values = c("red", "black")) +
    theme(
        legend.position = "bottom",
        legend.background = element_rect(fill = "#65737e"),
        legend.text = element_text(color = "white"),
        legend.title = element_text(color = "white"),
        panel.background = element_rect(fill = "#65737e"),
        panel.grid.major = element_line(color = "#65737e"),
        panel.grid.minor = element_line(color = "#65737e"),
        plot.background = element_rect(fill = "#65737e"),
        axis.text.x = element_text(color = "white"),
        axis.text.y = element_text(color = "white"),
        axis.title.x = element_text(color = "white"),
        axis.title.y = element_text(color = "white"),
        title = element_text(color = "white")
    ) +
    labs(
        title = "How many members visited and communicated?",
        subtitle = "S1 and S2",
        x = "",
        color = "Legend",
        caption = "data: BanklessDAO Discord | visual: @paulapivat, Analytics Guild"
    )

```


## Total Message - Avg Message: S1 and S2

Average Messages going down

```{r, echo=FALSE}

# JOIN Message - Avg Message: S1 and S2 ----

msg_avg_s1 <- read_csv("../s2_data_activity/discord/raw_data/message-avg-msg_290921.csv")
msg_avg_s2 <- read_csv("./discord/raw_data/guild-message-activity_010122.csv")

total_msg_avg <- rbind(msg_avg_s1, msg_avg_s2)

total_msg_avg %>%
    rename(
        time = "interval_start_timestamp",
        per = "messages_per_communicator"
    ) %>%
    ggplot(aes(x = time)) +
    geom_bar(aes(y = messages, color = "Messages sent"), stat = "identity", fill = "black") +
    # conversion between two y-axis (similar to % conversion)
    geom_line(aes(y = per*6000/12, color = "Messages per communicator"), size = 1.5) +
    geom_line(y = 5000, color = "orange", size = 0.2) +
    # vertical line separating season 1 v season 2
    geom_vline(xintercept = as.POSIXct("2021-10-04", origin = "yyyy-mm-dd"), color = 'white', size = 1.5, linetype = 'dotted') +
    scale_y_continuous(
        name = "Messages sent",
        sec.axis = sec_axis(trans = ~./6000*12, name = "Message per ommunicator")
    ) +
    scale_color_manual(values = c("red", "black")) +
    theme(
        legend.position = "bottom",
        legend.background = element_rect(fill = "#65737e"),
        legend.text = element_text(color = "white"),
        legend.title = element_text(color = "white"),
        panel.background = element_rect(fill = "#65737e"),
        panel.grid.major = element_line(color = "#65737e"),
        panel.grid.minor = element_line(color = "#65737e"),
        plot.background = element_rect(fill = "#65737e"),
        axis.text.x = element_text(color = "white"),
        axis.text.y = element_text(color = "white"),
        axis.title.x = element_text(color = "white"),
        axis.title.y = element_text(color = "white"),
        title = element_text(color = "white")
    ) +
    labs(
        title = "Message Activity",
        subtitle = "S1 and S2",
        x = "",
        color = "Legend",
        caption = "data: BanklessDAO Discord | visual: @paulapivat, Analytics Guild"
    )
```


## Total Voice Activity: S1 and S2

```{r, echo=FALSE}
# JOIN Voice Activity S1 and S2 ----

voice_act_s1 <- read_csv("../s2_data_activity/discord/raw_data/voice-activity_290921.csv")
voice_act_s2 <- read_csv("./discord/raw_data/guild-voice-activity_010122.csv")

total_voice_act <- rbind(voice_act_s1, voice_act_s2)

total_voice_act %>%
    rename(
        time = "interval_start_timestamp",
        speak = "speaking_minutes"
    ) %>%
    ggplot(aes(x = time)) +
    geom_bar(aes(y = speak), stat = "identity", fill = "white") +
    # vertical line separating season 1 v season 2
    geom_vline(xintercept = as.POSIXct("2021-10-04", origin = "yyyy-mm-dd"), color = 'red', size = 1.5, linetype = 'dotted') +
    theme(
        panel.background = element_rect(fill = "#65737e"),
        panel.grid.major = element_line(color = "#65737e"),
        panel.grid.minor = element_line(color = "#65737e"),
        plot.background = element_rect(fill = "#65737e"),
        axis.text.x = element_text(color = "white"),
        axis.text.y = element_text(color = "white"),
        axis.title.x = element_text(color = "white"),
        axis.title.y = element_text(color = "white"),
        title = element_text(color = "white")
    ) +
    labs(
        title = "Voice Activity: S1 and S2",
        subtitle = "Speaking minutes",
        y = "Values",
        x = "",
        caption = "data: BanklessDAO Discord | visual: @paulapivat, Analytics Guild"
    )

```

## Snapshot Votes: Season 0 and Season 1: Transform data

```{r,echo=FALSE}
# load library ----
library(tidyverse)

# load data ----
p1 <- read_csv("../s2_data_activity/snapshot/raw_data/snapshot-report-12389500.csv")
p2 <- read_csv("../s2_data_activity/snapshot/raw_data/snapshot-report-12381760.csv")
p3 <- read_csv("../s2_data_activity/snapshot/raw_data/snapshot-report-12414778.csv")
p4 <- read_csv("../s2_data_activity/snapshot/raw_data/snapshot-report-12597085.csv")
p5 <- read_csv("../s2_data_activity/snapshot/raw_data/snapshot-report-12655510.csv")
p6 <- read_csv("../s2_data_activity/snapshot/raw_data/snapshot-report-12742069.csv")
p7 <- read_csv("../s2_data_activity/snapshot/raw_data/snapshot-report-12822029.csv")
p8 <- read_csv("../s2_data_activity/snapshot/raw_data/snapshot-report-12921898.csv")
p9 <- read_csv("../s2_data_activity/snapshot/raw_data/snapshot-report-13238616.csv")
p10 <- read_csv("../s2_data_activity/snapshot/raw_data/snapshot-report-13239761.csv")

# data wrangling ----

# select two columns needed (address, balance $BANK)
# add column proposal number
# add column proposal full name
# save as new data frame
# join into one data frame

sp1 <- p1 %>%
    select(address, balance) %>%
    mutate(
        num = "proposal 1",
        name = "Approve the Bankless DAO Genesis Proposal"
    )

sp2 <- p2 %>%
    select(address, balance) %>%
    mutate(
        num = "proposal 2",
        name = "What charity should CMS Holdings donate 100k towards"
    )

sp3 <- p3 %>%
    select(address, balance) %>%
    mutate(
        num = "proposal 3",
        name = "Badge Distribution for Second Airdrop"
    )


sp4 <- p4 %>%
    select(address, balance) %>%
    mutate(
        num = "proposal 4",
        name = "Reward Season 0 Active Members"
    )


sp5 <- p5 %>%
    select(address, balance) %>%
    mutate(
        num = "proposal 5",
        name = "Bankless DAO Season 1"
    )


sp6 <- p6 %>%
    select(address, balance) %>%
    mutate(
        num = "proposal 6",
        name = "BanklessDAO Season 1 Grants Committee Ratification"
    )

sp7 <- p7 %>%
    select(address, balance) %>%
    mutate(
        num = "proposal 7",
        name = "BED Index Logo Contest"
    )

sp8 <- p8 %>%
    select(address, balance) %>%
    mutate(
        num = "proposal 8",
        name = "Request for funds for Notion's ongoing subscription"
    )


sp9 <- p9 %>%
    select(address, balance) %>%
    mutate(
        num = "proposal 9",
        name = "Transfer ownership of the treasury multisig wallet from the genesis team to the DAO"
    )


sp10 <- p10 %>%
    select(address, balance) %>%
    mutate(
        num = "proposal 10",
        name = "Bankless DAO Season 2"
    )

# combine new data frames ----

snapshot_votes_s1 <- rbind(sp1, sp2, sp3, sp4, sp5, sp6, sp7, sp8, sp9, sp10) 

# re-arrange factor levels
# specify factor order (proposal #'s)
library(forcats)

# manually arranging factors - num
# note: move "proposal 10" to the end
# them apply newly arranged factor levels to column of interest
snapshot_votes_s1$num <- fct_relevel(snapshot_votes_s1$num, c("proposal 1", "proposal 2", "proposal 3", "proposal 4", "proposal 5", 
                       "proposal 6", "proposal 7", "proposal 8", "proposal 9", "proposal 10"))


# manually arrange factors - name
# then apply newly arranged factor levels to column of interest
snapshot_votes_s1$name <- fct_relevel(snapshot_votes_s1$name, c("Approve the Bankless DAO Genesis Proposal",
                        "What charity should CMS Holdings donate 100k towards",
                        "Badge Distribution for Second Airdrop",
                        "Reward Season 0 Active Members",
                        "Bankless DAO Season 1",
                        "BanklessDAO Season 1 Grants Committee Ratification",
                        "BED Index Logo Contest",
                        "Request for funds for Notion's ongoing subscription",
                        "Transfer ownership of the treasury multisig wallet from the genesis team to the DAO",
                        "Bankless DAO Season 2"))

```


## Snapshot Votes: Season 0 and Season 1: Visualize data

Note: See above for data wrangling and transformation.

```{r,echo=FALSE}
# visualize num addresses vote ----

snapshot_votes_s1 %>%
    count(name) %>%
    ggplot(aes(x = n, y = name, fill = name)) +
    geom_col() +
    geom_text(aes(label = n), hjust = -0.2, color = "white") +
    theme(
        legend.position = "none",
        panel.background = element_rect(fill = "#65737e"),
        panel.grid.major = element_line(color = "#65737e"),
        panel.grid.minor = element_line(color = "#65737e"),
        plot.background = element_rect(fill = "#65737e"),
        axis.text.x = element_text(color = "white"),
        axis.text.y = element_text(color = "white", size = 15),
        axis.title.x = element_text(color = "white"),
        axis.title.y = element_text(color = "white"),
        title = element_text(color = "white", face = "bold")
    ) +
    scale_y_discrete(limits = rev(levels(snapshot_votes_s1$name))) +
    scale_fill_manual(values = c("#ffb2b2", "#ffb2b2", "#ffb2b2", "#ffb2b2", "#ffb2b2", 
                                 "#ffb2b2", "#ffb2b2", "#ffb2b2", "#ffb2b2", "#ffb2b2")) +
    labs(
        title = "Member Participation in Snapshot Votes",
        subtitle = "Season 0 - Season 1",
        y = "",
        x = "Number of Addresses"
    )
```


## Transform & Wrangle Snapshot Votes: Season 2

Data from DaoDash: `Snapshot S2` query. 

Data: analytics/s3_data_activity/snapshot/raw_data

```{r, echo=FALSE}
# snapshot data
# snapshot_votes_s2 <- read_csv("./snapshot/raw_data/snapshot_votes_s2_010122.csv") -- old version
snapshot_votes_s2 <- read_csv("./snapshot/raw_data/snapshot_votes_s2_20220117T075716.csv")


snapshot_votes_s2_fct <- snapshot_votes_s2 %>%
    group_by(title) %>%
    tally(sort = TRUE) %>%
    rename(
        name = title
    )

# re-order factor levels

# Season 0 & 1 (order, top to bottom)

#Approve the Bankless DAO Genesis Proposal	1240			
#What charity should CMS Holdings donate 100k towards	597			
#Badge Distribution for Second Airdrop	588			
#Reward Season 0 Active Members	558			
#Bankless DAO Season 1	509			
#BanklessDAO Season 1 Grants Committee Ratification	136			
#BED Index Logo Contest	196			
#Request for funds for Notion's ongoing subscription	109			
#Transfer ownership of the treasury multisig wallet from the genesis team to the DAO	650			
#Bankless DAO Season 2	752	

# Season 2 (order, top to bottom)

# Bankless DAO Season 2 Grants Committee Ratification
# Bankless DAO Treasury Multi-sig Signer Ratification
# S1 & S2 Grants Committee Compensation
# Retro Rectification Donations
# Season 2 Project and Guild Funding
# Balancer Liquidity Mining Program
# Olympus Pro BANK liquidity bonds,
# Execute swap with Tokemak for BANK reactor ignition
# Funding for Season 2 Approved Projects
# BanklessDAO Season 3 Specification
# Firming Up Governance
# Season 3 Grants Committee Elections
# Season 3 Project and Guild Funding ----------STILL ACTIVE VOTING
# --- pending ---


# manually arrange factors - name
# then apply newly arranged factor levels to column of interest
snapshot_votes_s2_fct$name <- fct_relevel(snapshot_votes_s2_fct$name, c("Bankless DAO Season 2 Grants Committee Ratification",
                        "Bankless DAO Treasury Multi-sig Signer Ratification",
                        "S1 & S2 Grants Committee Compensation",
                        "Retro Rectification Donations",
                        "Season 2 Project and Guild Funding",
                        "Balancer Liquidity Mining Program",
                        "Olympus Pro BANK liquidity bonds",
                        "Execute swap with Tokemak for BANK reactor ignition",
                        "Funding for Season 2 Approved Projects",
                        "BanklessDAO Season 3 Specification",
                        "Firming Up Governance",
                        "Season 3 Grants Committee Elections",
                        "Season 3 Project and Guild Funding"
                         ))



```


## Visualize Snapshot Votes: Season 2

Use: `snapshot_votes_s2_fct`, still pending 5 more snapshot vote events

- Funding for Season 2 Approved Projects
- BanklessDAO Season 3 Specification
- Firming Up Governance
- Season 3 Grants Committee Elections
- Season 3 Project and Guild Funding

```{r, echo=FALSE}

snapshot_votes_s2_fct %>%
    ggplot(aes(x = n, y = name, fill = name)) +
    geom_col() +
    geom_text(aes(label = n), hjust = -0.2, color = "white") +
    theme(
        legend.position = "none",
        panel.background = element_rect(fill = "#65737e"),
        panel.grid.major = element_line(color = "#65737e"),
        panel.grid.minor = element_line(color = "#65737e"),
        plot.background = element_rect(fill = "#65737e"),
        axis.text.x = element_text(color = "white"),
        axis.text.y = element_text(color = "white"),
        axis.title.x = element_text(color = "white"),
        axis.title.y = element_text(color = "white", size = 15),
        title = element_text(color = "white", face = "bold")
    ) +
    scale_y_discrete(limits = rev(levels(snapshot_votes_s2_fct$name))) +
    scale_fill_manual(values = c("#ffb2b2", "#ffb2b2", "#ffb2b2", "#ffb2b2", "#ffb2b2", 
                                 "#ffb2b2", "#ffb2b2", "#ffb2b2", "#ffb2b2", "#ffb2b2",
                                 "#ffb2b2", "#ffb2b2", "#ffb2b2")) +
    labs(
        title = "Member Participation in Snapshot Votes",
        subtitle = "Season 2",
        y = "",
        x = "Number of Addresses"
    )

```

## Snapshot Votes across Season 0 - 2

Combine data sets

```{r, echo=FALSE}

library(tidyverse)

total_snapshot_votes <- read_csv("./snapshot/raw_data/total_snapshot_votes_s0_s2_20220117T103145.csv")


total_snapshot_votes_fct <- total_snapshot_votes %>%
    group_by(title) %>%
    tally(sort = TRUE) %>%
    rename(
        name = title
    )


# set factor order
total_snapshot_votes_fct$name <- fct_relevel(total_snapshot_votes_fct$name, c("Approve the Bankless DAO Genesis Proposal?",
                        "What charity should CMS Holdings donate 100k towards?",
                        "Badge Distribution for Second Airdrop",
                        "Reward Season 0 Active Members",
                        "Bankless DAO Season 1",
                        "Title: BanklessDAO Season 1 Grants Committee ratification",
                        "BED Index Logo Contest",
                        "Request for funds for Notion’s ongoing subscription",
                        "Transfer ownership of the treasury multisig wallet from the genesis team to the DAO.",
                        "Bankless DAO Season 2",
                        "Bankless DAO Season 2 Grants Committee Ratification",
                        "Bankless DAO Treasury Multi-sig Signer Ratification",
                        "S1 & S2 Grants Committee Compensation",
                        "Retro Rectification Donations",
                        "Season 2 Project and Guild Funding",
                        "Balancer Liquidity Mining Program",
                        "Olympus Pro BANK liquidity bonds",
                        "Execute swap with Tokemak for BANK reactor ignition",
                        "Funding for Season 2 Approved Projects",
                        "BanklessDAO Season 3 Specification",
                        "Firming Up Governance",
                        "Season 3 Grants Committee Elections",
                        "Season 3 Project and Guild Funding"))

# find average snapshot votes across proposal
# avg = 11136 (sum) / 23 (number of proposals)
total_snapshot_votes_fct %>%
    summarize(avg = sum(n))



# visualize
total_snapshot_votes_fct %>%
    ggplot(aes(x = n, y = name, fill = name)) +
    geom_col() +
    geom_text(aes(label = n), hjust = -0.2, color = "white") +
    # vertical line separating season 1 v season 2
    geom_vline(xintercept = 484, color = 'white', size = 1, linetype = 'dotted') +
    theme(
        legend.position = "none",
        panel.background = element_rect(fill = "#65737e"),
        panel.grid.major = element_line(color = "#65737e"),
        panel.grid.minor = element_line(color = "#65737e"),
        plot.background = element_rect(fill = "#65737e"),
        axis.text.x = element_text(color = "white"),
        axis.text.y = element_text(color = "white", size = 13),
        axis.title.x = element_text(color = "white"),
        axis.title.y = element_text(color = "white", size = 15),
        title = element_text(color = "white")
    ) +
    scale_y_discrete(limits = rev(levels(total_snapshot_votes_fct$name))) +
    scale_fill_manual(values = c("#ffb2b2", "#ffb2b2", "#ffb2b2", "#ffb2b2", "#ffb2b2", 
                                 "#ffb2b2", "#ffb2b2", "#ffb2b2", "#ffb2b2", "#ffb2b2",
                                 "#ffb2b2", "#ffb2b2", "#ffb2b2","#ffb2b2", "#ffb2b2",
                                 "#ffb2b2", "#ffb2b2", "#ffb2b2", "#ffb2b2", "#ffb2b2", 
                                 "#ffb2b2", "#ffb2b2", "#ffb2b2")) +
    labs(
        title = "Member Participation in Snapshot Votes",
        subtitle = "Total: Season 0 - Season 2",
        y = "",
        x = "Number of Addresses",
        caption = "visual: @paulapivat | Powered by: DAODash "
    )



```


## Grants Committee Fund Distribution: Stacked Bar Chart

Note: For comparison between S1 and S2 where available.

SQL Query: See DaoDash `Fund_Flow_GC_2`. Note dates between S1 and S2. Same query used for Sankey.

**NOTE**: May need to add Treasury Guild as another potential source of funds (confirm Treasury address).

```{r}
# --Season 1 (116 rows): timestamp_display < '2021-10-08'::DATE AND timestamp_display > '2021-06-14'::DATE  -- TOTAL: 11,288,361.28706
# --Season 2 (426 rows): timestamp_display > '2021-10-07'::DATE AND timestamp_display < '2022-01-08'::DATE  -- TOTAL: 10,780,178.00001

#WITH fund_flow AS (
#select 
#  'Out' as Direction,
#   ssb.from_address,
#   w.human_readable,
#   w.entity_type,
#   ssb.amount_display,
#   ssb.timestamp_display,
#   ssb.to_address
#from stg_subgraph_bank_1 ssb
#join public.bankless_wallet_entity_2 w on lower(ssb.from_address) = lower(w.wallet_address)
#-- note 'Out' is from_address
   
#union all 
   
#select 
#  'In' as Direction,
#  ssb.from_address,
#  w.human_readable,
#  w.entity_type,
#  ssb.amount_display,
#  ssb.timestamp_display,
#  ssb.to_address
#from stg_subgraph_bank_1 ssb
#join public.bankless_wallet_entity_2 w on lower(ssb.to_address) = lower(w.wallet_address)
#-- note 'In' is to_address
#),

#gcs1 AS (
#SELECT
#  direction,
#  from_address,
#  human_readable AS readable,
#  entity_type,
#  amount_display,
#  timestamp_display,
#  to_address
#FROM fund_flow 
#WHERE entity_type = 'Grants Committee'
#AND timestamp_display > '2021-10-07'::DATE  
#AND timestamp_display < '2022-01-08'::DATE
#AND direction = 'Out'
#--where timestamp_display > '2021-10-01T09:26:59'::TIMESTAMP 
#ORDER BY timestamp_display DESC
#)

#SELECT
#  g.direction,
#  g.from_address,
#  g.readable,
#  g.entity_type,
#  g.amount_display,
#  g.timestamp_display,
#  g.to_address,
#  b.human_readable 
#FROM gcs1 g 
#LEFT JOIN bankless_wallet_entity_2 b ON lower(g.to_address) = lower(b.wallet_address)
```

Visualization

```{r, echo=FALSE}
library(tidyverse)
library(scales)

# load data
gcs1 <- read_csv("./sankey/raw_data/s1_fund_flow_gc_2_20220112T062448.csv")
gcs2 <- read_csv("./sankey/raw_data/s2_fund_flow_gc_2_20220112T063018.csv")

# transform
gcs1a <- gcs1 %>%
    mutate(
        season = 1,
        human_readable = if_else(is.na(human_readable), "Misc", human_readable)
    ) %>% 
    select(human_readable, amount_display, season)



gcs2a <- gcs2 %>%
    mutate(
        season = 2,
        human_readable = if_else(is.na(human_readable), "Misc", human_readable)
    ) %>% 
    select(human_readable, amount_display, season)

grants <- rbind(gcs1a, gcs2a)

# scientific notation
options(scipen=999)

# visualize
grants %>%
    mutate(
        season = as.factor(season)
    ) %>%
    group_by(human_readable, season) %>%
    summarise(amount = sum(amount_display)) %>%
    ggplot(aes(x = reorder(human_readable, amount), y = amount, fill = season)) +
    geom_bar(stat = "identity", position = "stack") +
    scale_y_continuous(labels = comma) +
    coord_flip() +
    theme_minimal()
```

## Bankless Vault Fund Distribution

**Note**: In Season 1, Analytics Guild received funds from the Grants Committee address, in Season 2, the Analytics Guild received funds from the Bankless Vault address.

See DaoDash: `Fund_Flow_Bankless_Vault` (nearly identical to `Fund_Flow_GC_2`, except direction is 'In'). 

```{r, echo=FALSE}
library(tidyverse)
library(scales)

# load data
bv_s1 <- read_csv("./sankey/raw_data/s1_fund_flow_bankless_vault_20220113T082455.csv")
bv_s2 <- read_csv("./sankey/raw_data/s2_fund_flow_bankless_vault_20220113T082831.csv")

# transform
bv_s1a <- bv_s1 %>%
    mutate(
        season = 1
    ) %>%
    select(human_readable, amount_display, season)


bv_s2a <- bv_s2 %>%
    mutate(
        season = 2
    ) %>%
    select(human_readable, amount_display, season)


bv_grants <- rbind(bv_s1a, bv_s2a)

# scientific notation
options(scipen=999)

# visualize
bv_grants %>%
    mutate(
        season = as.factor(season)
    ) %>%
    group_by(human_readable, season) %>%
    summarise(amount = sum(amount_display)) %>%
    ggplot(aes(x = reorder(human_readable, amount), y = amount, fill = season)) +
    geom_bar(stat = "identity", position = "stack") +
    scale_y_continuous(labels = comma) +
    coord_flip() +
    theme_minimal()

# full grants - minus grants committee
full_grants <- rbind(gcs1a, gcs2a, bv_s1a, bv_s2a)

full_grants %>%
    mutate(
        season = as.factor(season)
    ) %>%
    group_by(human_readable, season) %>%
    summarise(amount = sum(amount_display)) %>%
    filter(human_readable != 'Grants Committee') %>%
    ggplot(aes(x = reorder(human_readable, amount), y = amount, fill = season)) +
    geom_bar(stat = "identity", position = "dodge") +
    scale_y_continuous(labels = comma) +
    coord_flip() +
    theme(
        legend.background = element_rect(fill = "#65737e"),
        legend.text = element_text(color = "white"),
        legend.title = element_text(color = "white"),
        panel.background = element_rect(fill = "#65737e"),
        panel.grid.major = element_line(color = "#65737e"),
        panel.grid.minor = element_line(color = "#65737e"),
        plot.background = element_rect(fill = "#65737e"),
        axis.text.x = element_text(color = "white"),
        axis.text.y = element_text(color = "white"),
        axis.title.x = element_text(color = "white"),
        axis.title.y = element_text(color = "white"),
        title = element_text(color = "white", face = "bold")
    ) +
    scale_fill_manual(values = c("black", "red")) +
    labs(
        title = "Funding from Grants Committee | Bankless Vault",
        subtitle = "S1 and S2",
        x = "Projects & Guilds",
        y = "Amount ($BANK)",
        caption = "Powered by DAO Dash"
    )

# coord flip
full_grants %>%
    mutate(
        season = as.factor(season)
    ) %>%
    group_by(human_readable, season) %>%
    summarise(amount = sum(amount_display)) %>%
    filter(human_readable != 'Grants Committee') %>%
    ggplot(aes(x = reorder(human_readable, amount), y = amount, fill = season)) +
    geom_bar(stat = "identity", position = "dodge") +
    scale_y_continuous(labels = comma) +
    theme(
        legend.background = element_rect(fill = "#65737e"),
        legend.text = element_text(color = "white"),
        legend.title = element_text(color = "white"),
        panel.background = element_rect(fill = "#65737e"),
        panel.grid.major = element_line(color = "#65737e"),
        panel.grid.minor = element_line(color = "#65737e"),
        plot.background = element_rect(fill = "#65737e"),
        axis.text.x = element_text(color = "white", angle = 40, hjust = 1, size = 12),
        axis.text.y = element_text(color = "white", size = 12),
        axis.title.x = element_text(color = "white"),
        axis.title.y = element_text(color = "white"),
        title = element_text(color = "white")
    ) +
    scale_fill_manual(values = c("white", "red")) +
    labs(
        title = "Funding from Grants Committee | Bankless Vault",
        subtitle = "S1 and S2",
        x = "Projects & Guilds",
        y = "Amount ($BANK)",
        caption = "visual: @paulapivat | Powered by: DAODash"
    )




```

## Example Sankey

```{r, echo=FALSE}
library(tidyverse)
library(networkD3)

# sample sankey ----

# flow
links <- data.frame(
    source=c("group_A","group_A", "group_B", "group_C", "group_C", "group_E"), 
    target=c("group_C","group_D", "group_E", "group_F", "group_G", "group_H"), 
    value=c(2,3, 2, 3, 1, 3)
)

# nodes
nodes <- data.frame(
    name=c(as.character(links$source), 
           as.character(links$target)) %>% unique()
)

# With networkD3, connection must be provided using id, not using real name like in the links dataframe.. So we need to reformat it.
links$IDsource <- match(links$source, nodes$name)-1 
links$IDtarget <- match(links$target, nodes$name)-1

# Make the Network
p <- sankeyNetwork(Links = links, Nodes = nodes,
              Source = "IDsource", Target = "IDtarget",
              Value = "value", NodeID = "name", 
              sinksRight=FALSE)
p

```

## Grants Committee Season 1 Sankey

Workflow

Step 1: Replace `NA` values. Note: `NA` values step from having new projects, guilds pop up after the creation of `bankless_wallet_entity` table in DaoDash, so be sure to update that table before proceeding. 

Step 2: =create a `my_links` table, 
Step 2a: a `my_nodes` table, 
Step 2b: create IDSource, IDTarget columns
Step 2c: create `my_color` object.

Step 3: Create sankey w/ SankeyNetwork() function and library.

**NOTE** For comparison between Grants Comm distribution S1 vs S2, use side-by-side bar chart. 


## Grants Committee Season 2 Sankey

NOTE: Need to consult this [sheet](https://docs.google.com/spreadsheets/d/1a6ZMclYkESWNwV7xNhT-LELwHtK28wo9f4xx-JGab5k/edit#gid=0) to add additional project, guild multisig & address to `bankless_wallet_entity` table in DAODash.



## REVISED Sankey: Grants Committee Vault, Season 1


NOTE: full_grants <- rbind(gcs1a, gcs2a, bv_s1a, bv_s2a)

- full_grants combines grants committee + bankless_vault, across s1 and s2
- start with full_grants 

```{r, echo=FALSE}
# REVISED Sankey with New Data ----
library(tidyverse)
library(networkD3)

# create id for each node
# Alternative way to replace NA values - this works

# Starting point 'full_grants'
my_links_1 <- full_grants %>%
    filter(season == 1) %>%
    filter(human_readable != 'Grants Committee') %>%
    mutate(
        source = 'Grants Committee Vault'
    ) %>%
    rename(
        target = human_readable,
        value = amount_display
    ) %>%
    select(source, target, value) 


# unique nodes
# find unique values in column
# change 'target' to 'name'
unique_nodes <- unique(my_links_1[c("target")]) %>%
    rename(
        name = target
    ) %>%
    print(n = 100)




# manually create nodes
# NOTE: 'Grants Committee Vault' is first row
my_nodes_1 <- data.frame(name = c(
    "Grants Committee Vault",
    "BountyBoard",                
    "A/V Guild",                     
    "Bankless Academy",              
    "Analytics Guild",               
    "Degen",                         
    "Bankless Loans",                
    "Writers Guild",                 
    "Devs Guild Multisig",           
    "Translators Guild",             
    "Treasury Guild",                
    "Ops Guild",                     
    "Design Guild",                  
    "Research Guild",                
    "Marketing Guild",               
    "First Quest",                   
    "Bankless Website Multisig",     
    "Liquity Project Multisig",      
    "S1 Coordinape",                 
    "BED Index",                     
    "BizDev Guild",                  
    "DAO Punks",                     
    "Crypto Sapiens",                
    "Legal Guild",                   
    "Education Guild Multisig",      
    "DevOps Infrastructure Multisig",
    "Balancer Multisig",             
    "Misc"  
))


# create id for each node ----
# links$IDsource <- match(links$source, nodes$name)-1 
# links$IDtarget <- match(links$target, nodes$name)-1

my_links_1$IDsource <- match(my_links_1$source, my_nodes_1$name)-1
my_links_1$IDtarget <- match(my_links_1$target, my_nodes_1$name)-1

# add color

my_color_1 <- 'd3.scaleOrdinal() .domain(["Grants Committee Vault",
                            "BountyBoard",                
                            "A/V Guild",                     
                            "Bankless Academy",              
                            "Analytics Guild",               
                            "Degen",                         
                            "Bankless Loans",                
                            "Writers Guild",                 
                            "Devs Guild Multisig",           
                            "Translators Guild",             
                            "Treasury Guild",                
                            "Ops Guild",                     
                            "Design Guild",                  
                            "Research Guild",                
                            "Marketing Guild",               
                            "First Quest",                   
                            "Bankless Website Multisig",     
                            "Liquity Project Multisig",      
                            "S1 Coordinape",                 
                            "BED Index",                     
                            "BizDev Guild",                  
                            "DAO Punks",                     
                            "Crypto Sapiens",                
                            "Legal Guild",                   
                            "Education Guild Multisig",      
                            "DevOps Infrastructure Multisig",
                            "Balancer Multisig",             
                            "Misc"]) .range(["red", 
                                             "#2ca25f", 
                                             "#66c2a4", 
                                             "#b2e2e2", 
                                             "#edf8fb", 
                                             "#8B8989",
                                             "#006d2c", 
                                             "#2ca25f", 
                                             "#66c2a4", 
                                             "#b2e2e2", 
                                             "#edf8fb", 
                                             "#8B8989",
                                             "blue", 
                                             "green",
                                             "#2ca25f", 
                                             "#66c2a4", 
                                             "#b2e2e2", 
                                             "#edf8fb", 
                                             "#8B8989",
                                             "#006d2c", 
                                             "#2ca25f", 
                                             "#66c2a4", 
                                             "#b2e2e2", 
                                             "#edf8fb", 
                                             "#8B8989",
                                             "blue", 
                                             "green",
                                             "yellow"
                                    ])'

# sankey
sankeyNetwork(Links = my_links_1, Nodes = my_nodes_1,
              Source = "IDsource", Target = "IDtarget",
              Value = "value", NodeID = "name", colourScale = my_color_1, 
              fontSize = 15, fontFamily = "Helvetica", sinksRight=FALSE)





```

## REVISED Sankey: Grants Committee Vault, Season 2

```{r, echo=FALSE}

# REVISED Sankey with New Data ----
library(tidyverse)
library(networkD3)

# create id for each node
# Alternative way to replace NA values - this works

# Starting point 'full_grants'
my_links_2 <- full_grants %>%
    filter(season == 2) %>%
    filter(human_readable != 'Grants Committee') %>%
    mutate(
        source = 'Grants Committee Vault'
    ) %>%
    rename(
        target = human_readable,
        value = amount_display
    ) %>%
    select(source, target, value) 

# unique nodes
# find unique values in column
# change 'target' to 'name'
unique_nodes_2 <- unique(my_links_2[c("target")]) %>%
    rename(
        name = target
    ) %>%
    print(n = 100)

# MANUALLY create nodes
# NOTE: 'Grants Committee Vault' is first row
my_nodes_2 <- data.frame(name = c(
    "Grants Committee Vault",
    "BountyBoard",				
    "A/V Guild",				
    "DaoDash",				
    "FightClub",				
    "Content Gateway",				
    "Writers Guild",				
    "Marketing Guild",				
    "S1 Coordinape",				
    "DAO Punks",				
    "Legal Guild",
    "Balancer Liquidity Mining Program Multisig",				
    "International Media Node Multisig",				
    "Book Club Multisig",				
    "Podcast Hatchery Multisig",				
    "Flipper Zone Multisig",				
    "Bankless Academy",				
    "Analytics Guild",				
    "Degen",				
    "Bankless Loans",
    "NewsletterTeam",				
    "Devs Guild Multisig",				
    "Translators Guild",				
    "Treasury Guild",				
    "Ops Guild",				
    "Design Guild",				
    "Research Guild",				
    "First Quest",				
    "Bankless Website Multisig",				
    "Liquity Project Multisig",
    "BED Index",				
    "BizDev Guild",				
    "Education Guild Multisig",				
    "DevOps Infrastructure Multisig",
    "Misc"
))

# create id for each node ----
# links$IDsource <- match(links$source, nodes$name)-1 
# links$IDtarget <- match(links$target, nodes$name)-1

my_links_2$IDsource <- match(my_links_2$source, my_nodes_2$name)-1
my_links_2$IDtarget <- match(my_links_2$target, my_nodes_2$name)-1


# add color

my_color_2 <- 'd3.scaleOrdinal() .domain([
                            "Grants Committee Vault",
                            "BountyBoard",				
                            "A/V Guild",				
                            "DaoDash",				
                            "FightClub",				
                            "Content Gateway",				
                            "Writers Guild",				
                            "Marketing Guild",				
                            "S1 Coordinape",				
                            "DAO Punks",				
                            "Legal Guild",
                            "Balancer Liquidity Mining Program Multisig",				
                            "International Media Node Multisig",				
                            "Book Club Multisig",				
                            "Podcast Hatchery Multisig",				
                            "Flipper Zone Multisig",				
                            "Bankless Academy",				
                            "Analytics Guild",				
                            "Degen",				
                            "Bankless Loans",
                            "NewsletterTeam",				
                            "Devs Guild Multisig",				
                            "Translators Guild",				
                            "Treasury Guild",				
                            "Ops Guild",				
                            "Design Guild",				
                            "Research Guild",				
                            "First Quest",				
                            "Bankless Website Multisig",				
                            "Liquity Project Multisig",
                            "BED Index",				
                            "BizDev Guild",				
                            "Education Guild Multisig",				
                            "DevOps Infrastructure Multisig",
                            "Misc"]) .range(["red", 
                                             "#2ca25f", 
                                             "#66c2a4", 
                                             "#b2e2e2", 
                                             "#edf8fb", 
                                             "#8B8989",
                                             "#006d2c", 
                                             "#2ca25f", 
                                             "#66c2a4", 
                                             "#b2e2e2", 
                                             "#edf8fb", 
                                             "#8B8989",
                                             "blue", 
                                             "green",
                                             "#2ca25f", 
                                             "#66c2a4", 
                                             "#b2e2e2", 
                                             "#edf8fb", 
                                             "#8B8989",
                                             "#006d2c", 
                                             "#2ca25f", 
                                             "#66c2a4", 
                                             "#b2e2e2", 
                                             "#edf8fb", 
                                             "#8B8989",
                                             "blue", 
                                             "green",
                                             "yellow",
                                             "#8B8989",
                                             "#006d2c", 
                                             "#2ca25f", 
                                             "#66c2a4", 
                                             "#b2e2e2", 
                                             "#edf8fb", 
                                             "#8B8989",
                                    ])'


# sankey
sankeyNetwork(Links = my_links_2, Nodes = my_nodes_2,
              Source = "IDsource", Target = "IDtarget",
              Value = "value", NodeID = "name", colourScale = my_color_2, 
              fontSize = 15, fontFamily = "Helvetica", sinksRight=FALSE)

```






## Number of Bank Holders (Membership Categories); S1 vs S2

**Task**: Compare S1 vs S2 on all membership categories.

**Challenge**: Inconsistent results using very similar queries across DaoDash, Dune Analytics and Google BigQuery. Use **Dune Analytics** for now, reconcile sources in S3.


See `mem_1_10K_bank_holdings_time_range` and other segments downloaded in raw csv. 
Data gathered from DAODash table.

See also: 
- BANK Holders 10 - 35K
- BANK Holders 35 - 150K
- BANK Holders 150K - 1.5M

```{r, echo=FALSE}
library(tidyverse)
library(lubridate)
library(zoo)

bank_sg <- read_csv("./bank_subgraph/raw_data/mem_1_10K_bank_holdings_time_range_20220102T062946.csv")

# turn time stamp into date
bank_sg %>%
    mutate(
        new_day = date(day)
    ) %>%
    group_by(new_day) %>%
    tally(sort = TRUE) %>%
    arrange(new_day) %>%
    mutate(
        cummulative = cumsum(n),
        change = n - lag(n,1,default = 0.0),
        series = cummulative + change
    )%>%
    ggplot(aes(x = new_day, y = series)) +
    geom_line() +
    scale_x_date(date_breaks = "1 month") +
    labs(
        title = "Number of BANK Holders overtime",
        subtitle = "1 - 10K BANK"
    )

?rollsum
```



## Coordinape Distribution

**Task**: Query comparison of tokens/bank distributed via Coordinape in S1 vs S2.

**Challenge**: See DaoDash query, `Seasonal Coordinape Distribution`

**Request**: Reach out to Saul for coordinape network visual growth s1 to s2.

Create dataframe / tibble.

```{r, echo=FALSE}
library(tidyverse)

coord_s1 <- read_csv("./coordinape/raw_data/s1_coordinape_distribution_20220112T121445.csv")
coord_s2 <- read_csv("./coordinape/raw_data/s2_coordinape_distribution_20220112T120953.csv")

# sum tokens distributed - Season 1: 192,076 , Season 2: 425,561
coord_s1 %>%
    summarise(sum_tokens = sum(tokens))

coord_s2 %>%
    summarise(sum_tokens = sum(tokens))

# how many senders, Season 1: n = 302, Season 2: 458
coord_s1 %>%
    group_by(sender_id) %>%
    tally(sort = TRUE)

coord_s1 %>%
    distinct(sender_id) %>%
    count()

coord_s2 %>%
    distinct(sender_id) %>%
    count()

# how many recipients, Season 1: n = 416, Season 2: n = 481
coord_s1 %>%
    distinct(recipient_id) %>%
    count()

coord_s2 %>%
    distinct(recipient_id) %>%
    count()


# create dataframes for Tokens distributed, Number of Senders and Number of Receivers 
season <- c("1", "2")
tokens_distributed <- c(192076, 425561)
num_senders <- c(302, 458)
num_receivers <- c(416, 481)

coord_df <- data.frame(season, tokens_distributed, num_senders, num_receivers)

# scientific notation
options(scipen=999)



# visualize tokens_distributed
coord_df %>%
    ggplot(aes(x = season, y = tokens_distributed, fill = season)) +
    geom_col() +
    geom_text(aes(label = scales::comma(tokens_distributed)), vjust = 1.3, color = "white", size = 12) +
    scale_fill_manual(values = c("black", "red")) +
    scale_y_continuous(labels = comma) +
    theme(
        legend.position = "none",
        panel.background = element_rect(fill = "#798f9b"),
        panel.grid.major = element_line(color = "#798f9b"),
        panel.grid.minor = element_line(color = "#798f9b"),
        plot.background = element_rect(fill = "#798f9b"),
        axis.text.x = element_text(color = "white", size = 15),
        axis.text.y = element_text(color = "white", size = 15),
        axis.title.x = element_text(color = "white"),
        axis.title.y = element_text(color = "white"),
        title = element_text(color = "white", size = 16)
    ) +
    labs(
        title = "Coordinape: Tokens Distributed",
        subtitle = "Season 1 vs Season 2",
        y = "Tokens Distributed",
        x = "Season",
        caption = "visual: @paulapivat | Powered by: DAODash"
    )

# visualize num_senders
coord_df %>%
    ggplot(aes(x = season, y = num_senders, fill = season)) +
    geom_col() +
    geom_text(aes(label = scales::comma(num_senders)), vjust = 1.3, color = "white", size = 12) +
    scale_fill_manual(values = c("black", "red")) +
    scale_y_continuous(labels = comma) +
    theme(
        legend.position = "none",
        panel.background = element_rect(fill = "#798f9b"),
        panel.grid.major = element_line(color = "#798f9b"),
        panel.grid.minor = element_line(color = "#798f9b"),
        plot.background = element_rect(fill = "#798f9b"),
        axis.text.x = element_text(color = "white", size = 15),
        axis.text.y = element_text(color = "white", size = 15),
        axis.title.x = element_text(color = "white"),
        axis.title.y = element_text(color = "white"),
        title = element_text(color = "white", size = 16)
    ) +
    labs(
        title = "Coordinape: Number of Senders",
        subtitle = "Season 1 vs Season 2",
        y = "Number of Senders",
        x = "Season",
        caption = "visual: @paulapivat | Powered by: DAODash"
    )

# visualize num_receivers
coord_df %>%
    ggplot(aes(x = season, y = num_receivers, fill = season)) +
    geom_col() +
    geom_text(aes(label = scales::comma(num_receivers)), vjust = 1.3, color = "white", size = 12) +
    scale_fill_manual(values = c("black", "red")) +
    scale_y_continuous(labels = comma) +
    theme(
        legend.position = "none",
        panel.background = element_rect(fill = "#798f9b"),
        panel.grid.major = element_line(color = "#798f9b"),
        panel.grid.minor = element_line(color = "#798f9b"),
        plot.background = element_rect(fill = "#798f9b"),
        axis.text.x = element_text(color = "white", size = 15),
        axis.text.y = element_text(color = "white", size = 15),
        axis.title.x = element_text(color = "white"),
        axis.title.y = element_text(color = "white"),
        title = element_text(color = "white", size = 16)
    ) +
    labs(
        title = "Coordinape: Number of Receivers",
        subtitle = "Season 1 vs Season 2",
        y = "Number of Receivers",
        x = "Season",
        caption = "visual: @paulapivat | Powered by: DAODash"
    )





```

## POAP Distribution

**Task**: Find number of POAPs claimed for Community Calls S1 vs S2

**Progress**: Query Content Gateway API endpoint: 

https://prod-content-gateway-api.herokuapp.com/api/v1/graphql

Query historical -> PoapV1 -> PoapTokenV1s

Can query all events containing "Bankless DAO Community" (for community call poaps), but still need to find *number of poaps* claimed at each event. 

Query: DAO Dash `bankless_poaps_w_count`

```{r, echo=FALSE}
library(tidyverse)

# load data
poap_cc <- read_csv("./poap_cc_claims/raw_data/poap_cc_claims_20220114T085045.csv")

# remove rows: 1, 11, 37
poap_cc_2 <- poap_cc[-c(1,11,37),]

# average number of poaps claimed per event
# sum: 7264, total event = 34 - 3 (missing data)
# avg = 7264 / 31 = ~ 234
poap_cc_2 %>%
    mutate(
        mint_count_2 = as.numeric(mint_count)
    ) %>%
    filter(!is.na(mint_count_2)) %>%
    summarise(total = sum(mint_count_2))

# arrange by id to sort poap events by id/date

poap_cc_2 %>%
    arrange(id) %>%
    mutate(
        mint_count_2 = as.numeric(mint_count)
    ) %>%
    ggplot(aes(x = reorder(name, id), y = mint_count_2)) +
    geom_col() +
    # vertical line separating season 1 v season 2
    geom_hline(yintercept = 234, color = 'red', size = 1.5, linetype = 'dotted') +
    theme(
        axis.text.x = element_text(hjust = 1),
        panel.background = element_rect(fill = "#798f9b"),
        panel.grid.major = element_line(color = "#798f9b"),
        panel.grid.minor = element_line(color = "#798f9b"),
        plot.background = element_rect(fill = "#798f9b"),
        axis.text.y = element_text(color = "white"),
        axis.title.x = element_text(color = "white"),
        axis.title.y = element_text(color = "white"),
        title = element_text(color = "white")
    ) +
    coord_flip() +
    labs(
        title = "BanklessDAO Community Calls",
        subtitle = "POAPs Claimed",
        y = "Number of POAPs",
        x = "Events",
        caption = "visual: @paulapivat | Powered by:                      "
    )





```

Query from Content Gateway API Endpoint. https://prod-content-gateway-api.herokuapp.com/api/v1/graphql

NOTE: Used POAP.xyz subgraph API

```{r, echo=FALSE}
# GraphiQL query
# {
#  historical{
#    PoapV1 {
#      PoapEventV1s(first: 200, where: {name: {contains: "Bankless DAO Community"}}){
#        data{
#          id,
#          fancyId,
#          name,
#          year,
#          eventHostId,
#          eventTemplateId,
#          eventUrl
#        }
#      }
#    }
#  }
#}




```

## Bounty Board

**Task**: Query total number of bounties and total value committed to bounties between S1 v S2.

**Challenge**: query from database in prod. WIP. 

Number of bounties:                 S1: 40, S2: 66+

Value committed to bounties:        S1: 68K, S2: 209K

Update: 15/01/22 for numbers

```{r, echo=FALSE}

season <- c('1','2')
num_bounties <- c(40, 69)
value_in_bounties <- c(68071, 215506)


bb_df <- data.frame(season, num_bounties, value_in_bounties)


# geom_text(aes(label = count), position = position_stack(vjust = 1.5), color = "white")

# number of bounties: s1 vs s2
bb_df %>%
    ggplot(aes(x = season, y = num_bounties, fill = season)) +
    geom_col() +
    geom_text(aes(label = num_bounties), vjust = 1.3, color = "white", size = 15) +
    scale_fill_manual(values = c("black", "red")) +
    theme(
        legend.position = "none",
        panel.background = element_rect(fill = "#798f9b"),
        panel.grid.major = element_line(color = "#798f9b"),
        panel.grid.minor = element_line(color = "#798f9b"),
        plot.background = element_rect(fill = "#798f9b"),
        axis.text.x = element_text(color = "white", size = 15),
        axis.text.y = element_text(color = "white", size = 15),
        axis.title.x = element_text(color = "white"),
        axis.title.y = element_text(color = "white"),
        title = element_text(color = "white", size = 16)
    ) +
    labs(
        title = "Number of Bounties Posted",
        subtitle = "Season 1 vs Season 2",
        y = "Number of Bounties",
        x = "Season",
        caption = "data: BanklessDAO Bounty Board | visual: @paulapivat"
    )

# value in bounties: s1 vs s2
bb_df %>%
    ggplot(aes(x = season, y = value_in_bounties, fill = season)) +
    geom_col() +
    geom_text(aes(label = scales::comma(value_in_bounties)), vjust = 1.3, color = "white", size = 12) +
    scale_fill_manual(values = c("black", "red")) +
    scale_y_continuous(labels = comma) +
    theme(
        legend.position = "none",
        panel.background = element_rect(fill = "#798f9b"),
        panel.grid.major = element_line(color = "#798f9b"),
        panel.grid.minor = element_line(color = "#798f9b"),
        plot.background = element_rect(fill = "#798f9b"),
        axis.text.x = element_text(color = "white", size = 15),
        axis.text.y = element_text(color = "white", size = 15),
        axis.title.x = element_text(color = "white"),
        axis.title.y = element_text(color = "white"),
        title = element_text(color = "white", size = 16)
    ) +
    labs(
        title = "Total Value Committed to Bounties",
        subtitle = "Season 1 vs Season 2",
        y = "Value Committed (BANK)",
        x = "Season",
        caption = "data: BanklessDAO Bounty Board | visual: @paulapivat"
    )





```

## Discourse

Task: Connect to API to query forum posts with polls and number of people voting.

Challenge: API documentation does not mention Polls or Votes. See [documentation](https://docs.discourse.org/) here. 

Progress: Established API connection with the `pydiscourse` https://github.com/BanklessDAO/analytics/blob/main/discourse_forum/api_connection.py

Ended up downloading CSV manually of all users, instead of votes, will track other engagement metrics like: 
- topics_entered
- posts_read_count
- time_read
- topic_count

*note*: remove email column, then save raw data to github

```{r, echo=FALSE}

```


## First Quest

Task: Query number of new members going through First Quest 

**Challenge**: Data inserted at 2021-11-18, might have insufficient data to make S1 vs S2 comparison. 

Just show S2 First Quest data standalone (compare Funnel shape from two time periods).

```{r, echo=FALSE}

```


## Tips Given & Received

**Task**: Get comparison between S1 and S2, create tibble/dataframe to display data. 

**Data**: See DaoDash query: `Seasonal Tip Distribution` 

Season 1 Tip Distribution (2873 rows, 983,019 tips given), WHERE timestamp < '2021-10-08'::DATE AND timestamp > '2021-06-14'::DATE 

Season 2 Tip Distribution (1336 rows, 337,173 tips given), WHERE timestamp > '2021-10-07'::DATE AND timestamp < '2022-01-08'::DATE 



```{r, echo=FALSE}
tips_df <- data.frame(season = c("1", "2"), tips_distributed = c(983019, 337173))

tips_df %>%
    ggplot(aes(x = season, y = tips_distributed, fill = season)) +
    geom_col() +
    geom_text(aes(label = scales::comma(tips_distributed)), vjust = 1.3, color = "white", size = 12) +
    scale_fill_manual(values = c("black", "red")) +
    scale_y_continuous(labels = comma) +
    theme(
        legend.position = "none",
        panel.background = element_rect(fill = "#798f9b"),
        panel.grid.major = element_line(color = "#798f9b"),
        panel.grid.minor = element_line(color = "#798f9b"),
        plot.background = element_rect(fill = "#798f9b"),
        axis.text.x = element_text(color = "white", size = 15),
        axis.text.y = element_text(color = "white", size = 15),
        axis.title.x = element_text(color = "white"),
        axis.title.y = element_text(color = "white"),
        title = element_text(color = "white", size = 16)
    ) +
    labs(
        title = "Total Tips Distributed",
        subtitle = "Season 1 vs Season 2",
        y = "Tips Distributed",
        x = "Season",
        caption = "visual: @paulapivat | Powered by: DAODash"
    )





```

## Next Section

```{r, echo=FALSE}

```


## Next Section

```{r, echo=FALSE}

```


