---
title: "Spaces"
author: "Analytics Guild"
date: "01/01/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Setup

Loading libraries and data.

```{r, include=FALSE}
# load library ----
library(tidyverse)

# load data ----
new_member <- read_csv("./discord/raw_data/guild-joins-by-source_010122.csv")
total_member <- read_csv("./discord/raw_data/guild-total-membership_010122.csv")
first_activation <- read_csv("./discord/raw_data/guild-activation_010122.csv")
next_retention <- read_csv("./discord/raw_data/guild-retention_010122.csv")
visit_comm <- read_csv("./discord/raw_data/guild-communicators_010122.csv")
msg_avg <- read_csv("./discord/raw_data/guild-message-activity_010122.csv")
voice_act <- read_csv("./discord/raw_data/guild-voice-activity_010122.csv")

# snapshot data
snapshot_votes <- read_csv("./snapshot/raw_data/snapshot_votes_s2_010122.csv")
```


## New Members: S1 and S2

**Data Source**: Raw Data Discord Server Insights. Download CSV file to the following repo: analytics > s3_data_activity > discord > raw_data

**Procedure Summary**: For Season 1 vs Season 2 comparison, import two CSV datasets into dataframes. Combine those dataframes with `rbind`. Visualize using the `ggplot` `theme()` below. Include vertical line separating the two seasons. 

**Description of Finding**s: Showing organic grow in Discord discovery.



```{r, echo=FALSE}
# JOIN Discord Data S1 and S2 ----

new_member_s2 <- read_csv("../s2_data_activity/discord/raw_data/new-member-joins-by-source_290921.csv")
new_member_s3 <- read_csv("./discord/raw_data/guild-joins-by-source_010122.csv")

# combine s1 and s2
all_new_mem <- rbind(new_member_s2, new_member_s3)

# visualize
all_new_mem %>%
    rename(
        vanity = "vanity_joins",
        discovery = "discovery_joins",
        time = "interval_start_timestamp"
    ) %>%
    pivot_longer(cols = discovery:vanity, names_to = "channel", values_to = "count") %>%
    ggplot(aes(x = time, y = count, fill = channel)) +
    geom_bar(position = "stack", stat = "identity") +
    # geom_text(aes(label = count), position = position_stack(vjust = 1.5), color = "white") +
    # vertical line separating season 1 v season 2
    geom_vline(xintercept = as.POSIXct("2021-10-04", origin = "yyyy-mm-dd"), color = 'white', size = 1.5, linetype = 'dotted') +
    theme(
        legend.position = "bottom",
        legend.background = element_rect(fill = "#65737e"),
        legend.text = element_text(color = "white"),
        legend.title = element_text(color = "white"),
        panel.background = element_rect(fill = "#65737e"),
        panel.grid.major = element_line(color = "#65737e"),
        panel.grid.minor = element_line(color = "#65737e"),
        plot.background = element_rect(fill = "#65737e"),
        axis.text.x = element_text(color = "white"),
        axis.text.y = element_text(color = "white"),
        axis.title.x = element_text(color = "white"),
        axis.title.y = element_text(color = "white"),
        title = element_text(color = "white")
    ) +
    scale_fill_manual(values = c("white", "red", "black")) +
    labs(
        title = "How many new members are joining? (Seasons 1 - 2)",
        subtitle = "Where are they coming from?",
        y = "Joins",
        x = "",
        caption = "data: BanklessDAO Discord | visual: @paulapivat, Analytics Guild"
    )
```



# Total Members: S1 and S2

**Data Source**: Raw Data Discord Server Insights. Download CSV file to the following repo: analytics > s3_data_activity > discord > raw_data

**Procedure Summary**: For Season 1 vs Season 2 comparison, import two CSV datasets into dataframes. Combine those dataframes with `rbind`. Visualize using the `ggplot` `theme()` below. Include vertical line separating the two seasons. 

**Description of Finding**s: Total (cummulative) discord member numbers going up and to the right. Vertical line separting seasons. 


```{r, echo=FALSE}
# JOIN Total Member Growth S1 and S2 ----

total_member_s2 <- read_csv("../s2_data_activity/discord/raw_data/total-membership-joins_290921.csv")
total_member_s3 <- read_csv("./discord/raw_data/guild-total-membership_010122.csv")

all_total_mem <- rbind(total_member_s2, total_member_s3)

all_total_mem %>%
    rename(
        time = "interval_start_timestamp",
        total = "total_membership"
    ) %>%
    ggplot(aes(x = time)) +
    geom_line(aes(y = total), color = "red", size = 1.5) +
    geom_vline(xintercept = as.POSIXct("2021-10-04", origin = "yyyy-mm-dd"), color = 'white', size = 1.5, linetype = 'dotted') +
    theme(
        panel.background = element_rect(fill = "#65737e"),
        panel.grid.major = element_line(color = "#65737e"),
        panel.grid.minor = element_line(color = "#65737e"),
        plot.background = element_rect(fill = "#65737e"),
        axis.text.x = element_text(color = "white"),
        axis.text.y = element_text(color = "white"),
        axis.title.x = element_text(color = "white"),
        axis.title.y = element_text(color = "white"),
        title = element_text(color = "white")
    ) +
    labs(
        title = "Total membership over time: S1 and S2",
        y = "",
        x = "",
        caption = "data: BanklessDAO Discord | visual: @paulapivat, Analytics Guild"
    )

```


## First Day Activation: S1 and S2

**Data Source**: Raw Data Discord Server Insights. Download CSV file to the following repo: analytics > s3_data_activity > discord > raw_data

**Procedure Summary**: For Season 1 vs Season 2 comparison, import two CSV datasets into dataframes. Combine those dataframes with `rbind`. Visualize using the `ggplot` `theme()` below. Include vertical line separating the two seasons. 

**Description of Finding**s: Voice participation went up in Season 2:

```{r, echo=FALSE}
# JOIN Activation S1 and S2 ----

first_activation_s2 <- read_csv("../s2_data_activity/discord/raw_data/first-day-activation_290921.csv")
first_activation_s3 <- read_csv("./discord/raw_data/guild-activation_010122.csv")

total_activation <- rbind(first_activation_s2, first_activation_s3)

total_activation %>%
    rename(
        time = "interval_start_timestamp",
        new = "new_members",
        talked = "pct_communicated",
        visited = "pct_opened_channels"
    ) %>%
    ggplot(aes(x = time)) +
    geom_bar(aes(y = new, color = "New members"), stat = "identity", fill = "black") +
    geom_line(aes(y = talked*15, color = "% talked (voice or text)"), size = 1.5) +
    geom_line(aes(y = visited*15, color = "% visited more than 3 channels"), size = 1.5) +
    geom_line(y = 480, color = "orange", size = 0.2) +
    # vertical line separating season 1 v season 2
    geom_vline(xintercept = as.POSIXct("2021-10-04", origin = "yyyy-mm-dd"), color = 'white', size = 1.5, linetype = 'dotted') +
    scale_y_continuous(
        name = "New Members",
        sec.axis = sec_axis(trans = ~./1500*100, name = "% Activated")
    ) +
    scale_color_manual(values = c("white", "red", "black")) +
    theme(
        legend.position = "bottom",
        legend.background = element_rect(fill = "#65737e"),
        legend.text = element_text(color = "white"),
        legend.title = element_text(color = "white"),
        panel.background = element_rect(fill = "#65737e"),
        panel.grid.major = element_line(color = "#65737e"),
        panel.grid.minor = element_line(color = "#65737e"),
        plot.background = element_rect(fill = "#65737e"),
        axis.text.x = element_text(color = "white"),
        axis.text.y = element_text(color = "white"),
        axis.title.x = element_text(color = "white"),
        axis.title.y = element_text(color = "white"),
        title = element_text(color = "white")
    ) +
    labs(
        title = "How many new members successfully activate on their first day?",
        subtitle = "S1 and S2",
        x = "",
        color = "Legend",
        caption = "data: BanklessDAO Discord | visual: @paulapivat, Analytics Guild"
    )

```


## Total Retention: S1 and S2

**Data Source**: Raw Data Discord Server Insights. Download CSV file to the following repo: analytics > s3_data_activity > discord > raw_data

**Procedure Summary**: For Season 1 vs Season 2 comparison, import two CSV datasets into dataframes. Combine those dataframes with `rbind`. Visualize using the `ggplot` `theme()` below. Include vertical line separating the two seasons. 

**Description of Finding**s: Retention has not improved that much, but we have more new members. 

```{r, echo=FALSE}
# JOIN Retention S1 and S2 ----

next_retention_s1 <- read_csv("../s2_data_activity/discord/raw_data/next-week-retention_290921.csv")
next_retention_s2 <- read_csv("./discord/raw_data/guild-retention_010122.csv")

total_retention <- rbind(next_retention_s1, next_retention_s2)

total_retention %>%
    rename(
        time = "interval_start_timestamp",
        new = "new_members",
        retained = "pct_retained"
    ) %>%
    ggplot(aes(x = time)) +
    geom_bar(aes(y = new, color = "New members"), stat = "identity", fill = "black") +
    geom_line(aes(y = retained*15, color = "Week 1 retention (%)"), size = 1.5) +
    geom_line(y = 320, color = "orange", size = 0.2) +
    # vertical line separating season 1 v season 2
    geom_vline(xintercept = as.POSIXct("2021-10-04", origin = "yyyy-mm-dd"), color = 'white', size = 1.5, linetype = 'dotted') +
    scale_y_continuous(
        name = "New Members",
        sec.axis = sec_axis(trans = ~./1500*100, name = "Week 1 retention (%)")
    ) +
    scale_color_manual(values = c("black", "red")) +
    theme(
        legend.position = "bottom",
        legend.background = element_rect(fill = "#65737e"),
        legend.text = element_text(color = "white"),
        legend.title = element_text(color = "white"),
        panel.background = element_rect(fill = "#65737e"),
        panel.grid.major = element_line(color = "#65737e"),
        panel.grid.minor = element_line(color = "#65737e"),
        plot.background = element_rect(fill = "#65737e"),
        axis.text.x = element_text(color = "white"),
        axis.text.y = element_text(color = "white"),
        axis.title.x = element_text(color = "white"),
        axis.title.y = element_text(color = "white"),
        title = element_text(color = "white")
    ) +
    labs(
        title = "How many new members retain the next week?",
        subtitle = "S1 and S2",
        x = "",
        color = "Legend",
        caption = "data: BanklessDAO Discord | visual: @paulapivat, Analytics Guild"
    )
```



## Total Visitor and Communicator: S1 and S2

**Data Source**: Raw Data Discord Server Insights. Download CSV file to the following repo: analytics > s3_data_activity > discord > raw_data

**Procedure Summary**: For Season 1 vs Season 2 comparison, import two CSV datasets into dataframes. Combine those dataframes with `rbind`. Visualize using the `ggplot` `theme()` below. Include vertical line separating the two seasons. 

**Description of Finding**: Still below benchmark, but trending upward slight in season 2:

```{r, echo=FALSE}
# JOIN Visitors and Communicators: S1 and S2 ----

visit_comm_s1 <- read_csv("../s2_data_activity/discord/raw_data/visitors-communicators_290921.csv")
visit_comm_s2 <- read_csv("./discord/raw_data/guild-communicators_010122.csv")

total_visit_comm <- rbind(visit_comm_s1, visit_comm_s2)

total_visit_comm %>%
    rename(
        time = "interval_start_timestamp",
        comm = "pct_communicated"
    ) %>%
    ggplot(aes(x = time)) +
    geom_bar(aes(y = visitors, color = "Visitors"), stat = "identity", fill = "black") +
    geom_line(aes(y = comm*30, color = "% communicators"), size = 1.5) +
    geom_line(y = 1200, color = "orange", size = 0.2) +
    # vertical line separating season 1 v season 2
    geom_vline(xintercept = as.POSIXct("2021-10-04", origin = "yyyy-mm-dd"), color = 'white', size = 1.5, linetype = 'dotted') +
    scale_y_continuous(
        name = "Visitors",
        sec.axis = sec_axis(trans = ~./3000*100, name = "% Communicators")
    ) +
    scale_color_manual(values = c("red", "black")) +
    theme(
        legend.position = "bottom",
        legend.background = element_rect(fill = "#65737e"),
        legend.text = element_text(color = "white"),
        legend.title = element_text(color = "white"),
        panel.background = element_rect(fill = "#65737e"),
        panel.grid.major = element_line(color = "#65737e"),
        panel.grid.minor = element_line(color = "#65737e"),
        plot.background = element_rect(fill = "#65737e"),
        axis.text.x = element_text(color = "white"),
        axis.text.y = element_text(color = "white"),
        axis.title.x = element_text(color = "white"),
        axis.title.y = element_text(color = "white"),
        title = element_text(color = "white")
    ) +
    labs(
        title = "How many members visited and communicated?",
        subtitle = "S1 and S2",
        x = "",
        color = "Legend",
        caption = "data: BanklessDAO Discord | visual: @paulapivat, Analytics Guild"
    )

```


## Total Message - Avg Message: S1 and S2

**Data Source**: Raw Data Discord Server Insights. Download CSV file to the following repo: analytics > s3_data_activity > discord > raw_data

**Procedure Summary**: For Season 1 vs Season 2 comparison, import two CSV datasets into dataframes. Combine those dataframes with `rbind`. Visualize using the `ggplot` `theme()` below. Include vertical line separating the two seasons. 

**Description of Finding**: Average Messages per person trending down, but there are more messages in total in S2, relatively to S1.

```{r, echo=FALSE}

# JOIN Message - Avg Message: S1 and S2 ----

msg_avg_s1 <- read_csv("../s2_data_activity/discord/raw_data/message-avg-msg_290921.csv")
msg_avg_s2 <- read_csv("./discord/raw_data/guild-message-activity_010122.csv")

total_msg_avg <- rbind(msg_avg_s1, msg_avg_s2)

total_msg_avg %>%
    rename(
        time = "interval_start_timestamp",
        per = "messages_per_communicator"
    ) %>%
    ggplot(aes(x = time)) +
    geom_bar(aes(y = messages, color = "Messages sent"), stat = "identity", fill = "black") +
    # conversion between two y-axis (similar to % conversion)
    geom_line(aes(y = per*6000/12, color = "Messages per communicator"), size = 1.5) +
    geom_line(y = 5000, color = "orange", size = 0.2) +
    # vertical line separating season 1 v season 2
    geom_vline(xintercept = as.POSIXct("2021-10-04", origin = "yyyy-mm-dd"), color = 'white', size = 1.5, linetype = 'dotted') +
    scale_y_continuous(
        name = "Messages sent",
        sec.axis = sec_axis(trans = ~./6000*12, name = "Message per ommunicator")
    ) +
    scale_color_manual(values = c("red", "black")) +
    theme(
        legend.position = "bottom",
        legend.background = element_rect(fill = "#65737e"),
        legend.text = element_text(color = "white"),
        legend.title = element_text(color = "white"),
        panel.background = element_rect(fill = "#65737e"),
        panel.grid.major = element_line(color = "#65737e"),
        panel.grid.minor = element_line(color = "#65737e"),
        plot.background = element_rect(fill = "#65737e"),
        axis.text.x = element_text(color = "white"),
        axis.text.y = element_text(color = "white"),
        axis.title.x = element_text(color = "white"),
        axis.title.y = element_text(color = "white"),
        title = element_text(color = "white")
    ) +
    labs(
        title = "Message Activity",
        subtitle = "S1 and S2",
        x = "",
        color = "Legend",
        caption = "data: BanklessDAO Discord | visual: @paulapivat, Analytics Guild"
    )
```


## Total Voice Activity: S1 and S2

**Data Source**: Raw Data Discord Server Insights. Download CSV file to the following repo: analytics > s3_data_activity > discord > raw_data

**Procedure Summary**: For Season 1 vs Season 2 comparison, import two CSV datasets into dataframes. Combine those dataframes with `rbind`. Visualize using the `ggplot` `theme()` below. Include vertical line separating the two seasons. 

**Description of Finding**: Voice activity clearly went up in Season 2. 

```{r, echo=FALSE}
# JOIN Voice Activity S1 and S2 ----

voice_act_s1 <- read_csv("../s2_data_activity/discord/raw_data/voice-activity_290921.csv")
voice_act_s2 <- read_csv("./discord/raw_data/guild-voice-activity_010122.csv")

total_voice_act <- rbind(voice_act_s1, voice_act_s2)

total_voice_act %>%
    rename(
        time = "interval_start_timestamp",
        speak = "speaking_minutes"
    ) %>%
    ggplot(aes(x = time)) +
    geom_bar(aes(y = speak), stat = "identity", fill = "white") +
    # vertical line separating season 1 v season 2
    geom_vline(xintercept = as.POSIXct("2021-10-04", origin = "yyyy-mm-dd"), color = 'red', size = 1.5, linetype = 'dotted') +
    theme(
        panel.background = element_rect(fill = "#65737e"),
        panel.grid.major = element_line(color = "#65737e"),
        panel.grid.minor = element_line(color = "#65737e"),
        plot.background = element_rect(fill = "#65737e"),
        axis.text.x = element_text(color = "white"),
        axis.text.y = element_text(color = "white"),
        axis.title.x = element_text(color = "white"),
        axis.title.y = element_text(color = "white"),
        title = element_text(color = "white")
    ) +
    labs(
        title = "Voice Activity: S1 and S2",
        subtitle = "Speaking minutes",
        y = "Values",
        x = "",
        caption = "data: BanklessDAO Discord | visual: @paulapivat, Analytics Guild"
    )

```

## POAP Distribution

**Data Source**: McKethanor built a pipeline to the POAP Subgraph (w elixir), got the data and pushed to DAODash postgres database as `bankless_poaps_w_count`, with the columns: id, name and mint_count. You can filter for "bankless" and "community" to get events for Community Calls. 

**NOTE**: There is missing and/or incomplete data here. 

**Procedure Summary**: After querying DAODash and saving raw data in the Analytics Repo: analytics > s3_data_activity > poap_cc_claims > raw_data.

**Description of Finding**: Avg number of poaps claimed was 234 (up through Community Call #34). A lot of missing data still. 



```{r, echo=FALSE}
library(tidyverse)

# load data
poap_cc <- read_csv("./poap_cc_claims/raw_data/poap_cc_claims_20220114T085045.csv")

# remove rows: 1, 11, 37
poap_cc_2 <- poap_cc[-c(1,11,37),]

# average number of poaps claimed per event
# sum: 7264, total event = 34 - 3 (missing data)
# avg = 7264 / 31 = ~ 234
poap_cc_2 %>%
    mutate(
        mint_count_2 = as.numeric(mint_count)
    ) %>%
    filter(!is.na(mint_count_2)) %>%
    summarise(total = sum(mint_count_2))

# arrange by id to sort poap events by id/date

poap_cc_2 %>%
    arrange(id) %>%
    mutate(
        mint_count_2 = as.numeric(mint_count)
    ) %>%
    ggplot(aes(x = reorder(name, id), y = mint_count_2)) +
    geom_col() +
    # vertical line separating season 1 v season 2
    geom_hline(yintercept = 234, color = 'red', size = 1.5, linetype = 'dotted') +
    theme(
        axis.text.x = element_text(hjust = 1),
        panel.background = element_rect(fill = "#798f9b"),
        panel.grid.major = element_line(color = "#798f9b"),
        panel.grid.minor = element_line(color = "#798f9b"),
        plot.background = element_rect(fill = "#798f9b"),
        axis.text.y = element_text(color = "white"),
        axis.title.x = element_text(color = "white"),
        axis.title.y = element_text(color = "white"),
        title = element_text(color = "white")
    ) +
    coord_flip() +
    labs(
        title = "BanklessDAO Community Calls",
        subtitle = "POAPs Claimed",
        y = "Number of POAPs",
        x = "Events",
        caption = "visual: @paulapivat | Powered by:                      "
    )





```


**Alternative source**: Content Gateway API: https://prod-content-gateway-api.herokuapp.com/api/v1/graphql
Query historical -> PoapV1 -> PoapTokenV1s

Can query all events containing "Bankless DAO Community" (for community call poaps), but still need to find *number of poaps* claimed at each event. 

**NOTE**: Could also use POAP.xyz subgraph API - see hosted on TheGraph

```{r, echo=FALSE}
# GraphiQL query
# {
#  historical{
#    PoapV1 {
#      PoapEventV1s(first: 200, where: {name: {contains: "Bankless DAO Community"}}){
#        data{
#          id,
#          fancyId,
#          name,
#          year,
#          eventHostId,
#          eventTemplateId,
#          eventUrl
#        }
#      }
#    }
#  }
#}




```



## Snapshot Votes across Season 0 - 2

**Data Source**: Update 2 Snapshot related pipelines. First, update the pipeline **both** `snapshot_votes_sched.py` and `snapshot_proposal_sched.py` in repo: analytics > graphql > exploratory.

The pipelines feed into the following tables in postgres db:
- `stg_bankless_snapshot_1`
- `bankless_snapshot_header_1`

This is the query in DAODash:

```{python}
#SELECT
#  voter,
#  choice,
#  created,
#  vote_id,
#  title,
#  s.proposal_id 
#FROM stg_bankless_snapshot_1 s 
#LEFT JOIN bankless_snapshot_header_1 h ON s.proposal_id = h.proposal_id

```

Save download as CSV saved to this repo: s3_data_activity > snapshot > raw_data > total_snapshot_votes_s0_s2

**Procedure Summary**: The updated pipeline and query for `total_snapshot_votes_s0_s2` provides the raw data for visualization. Use the updated pipeline instead of trying to glue together separate data sets from S1 vs S2. 

**Description of Finding**: The average votes per Snapshot Proposal is 484. 10 of 23 proposals exceeded that amount. 

```{r, echo=FALSE}

library(tidyverse)

total_snapshot_votes <- read_csv("./snapshot/raw_data/total_snapshot_votes_s0_s2_20220117T103145.csv")


total_snapshot_votes_fct <- total_snapshot_votes %>%
    group_by(title) %>%
    tally(sort = TRUE) %>%
    rename(
        name = title
    )


# set factor order
total_snapshot_votes_fct$name <- fct_relevel(total_snapshot_votes_fct$name, c("Approve the Bankless DAO Genesis Proposal?",
                        "What charity should CMS Holdings donate 100k towards?",
                        "Badge Distribution for Second Airdrop",
                        "Reward Season 0 Active Members",
                        "Bankless DAO Season 1",
                        "Title: BanklessDAO Season 1 Grants Committee ratification",
                        "BED Index Logo Contest",
                        "Request for funds for Notion’s ongoing subscription",
                        "Transfer ownership of the treasury multisig wallet from the genesis team to the DAO.",
                        "Bankless DAO Season 2",
                        "Bankless DAO Season 2 Grants Committee Ratification",
                        "Bankless DAO Treasury Multi-sig Signer Ratification",
                        "S1 & S2 Grants Committee Compensation",
                        "Retro Rectification Donations",
                        "Season 2 Project and Guild Funding",
                        "Balancer Liquidity Mining Program",
                        "Olympus Pro BANK liquidity bonds",
                        "Execute swap with Tokemak for BANK reactor ignition",
                        "Funding for Season 2 Approved Projects",
                        "BanklessDAO Season 3 Specification",
                        "Firming Up Governance",
                        "Season 3 Grants Committee Elections",
                        "Season 3 Project and Guild Funding"))

# find average snapshot votes across proposal
# avg = 11136 (sum) / 23 (number of proposals)
total_snapshot_votes_fct %>%
    summarize(avg = sum(n))



# visualize
total_snapshot_votes_fct %>%
    ggplot(aes(x = n, y = name, fill = name)) +
    geom_col() +
    geom_text(aes(label = n), hjust = -0.2, color = "white") +
    # vertical line separating season 1 v season 2
    geom_vline(xintercept = 484, color = 'white', size = 1, linetype = 'dotted') +
    theme(
        legend.position = "none",
        panel.background = element_rect(fill = "#65737e"),
        panel.grid.major = element_line(color = "#65737e"),
        panel.grid.minor = element_line(color = "#65737e"),
        plot.background = element_rect(fill = "#65737e"),
        axis.text.x = element_text(color = "white"),
        axis.text.y = element_text(color = "white", size = 13),
        axis.title.x = element_text(color = "white"),
        axis.title.y = element_text(color = "white", size = 15),
        title = element_text(color = "white")
    ) +
    scale_y_discrete(limits = rev(levels(total_snapshot_votes_fct$name))) +
    scale_fill_manual(values = c("#ffb2b2", "#ffb2b2", "#ffb2b2", "#ffb2b2", "#ffb2b2", 
                                 "#ffb2b2", "#ffb2b2", "#ffb2b2", "#ffb2b2", "#ffb2b2",
                                 "#ffb2b2", "#ffb2b2", "#ffb2b2","#ffb2b2", "#ffb2b2",
                                 "#ffb2b2", "#ffb2b2", "#ffb2b2", "#ffb2b2", "#ffb2b2", 
                                 "#ffb2b2", "#ffb2b2", "#ffb2b2")) +
    labs(
        title = "Member Participation in Snapshot Votes",
        subtitle = "Total: Season 0 - Season 2",
        y = "",
        x = "Number of Addresses",
        caption = "visual: @paulapivat | Powered by: DAODash "
    )



```


## Grants Committee Fund Distribution: 


```{r}
# --Season 1 (116 rows): timestamp_display < '2021-10-08'::DATE AND timestamp_display > '2021-06-14'::DATE  -- TOTAL: 11,288,361.28706
# --Season 2 (426 rows): timestamp_display > '2021-10-07'::DATE AND timestamp_display < '2022-01-08'::DATE  -- TOTAL: 10,780,178.00001

#WITH fund_flow AS (
#select 
#  'Out' as Direction,
#   ssb.from_address,
#   w.human_readable,
#   w.entity_type,
#   ssb.amount_display,
#   ssb.timestamp_display,
#   ssb.to_address
#from stg_subgraph_bank_1 ssb
#join public.bankless_wallet_entity_2 w on lower(ssb.from_address) = lower(w.wallet_address)
#-- note 'Out' is from_address
   
#union all 
   
#select 
#  'In' as Direction,
#  ssb.from_address,
#  w.human_readable,
#  w.entity_type,
#  ssb.amount_display,
#  ssb.timestamp_display,
#  ssb.to_address
#from stg_subgraph_bank_1 ssb
#join public.bankless_wallet_entity_2 w on lower(ssb.to_address) = lower(w.wallet_address)
#-- note 'In' is to_address
#),

#gcs1 AS (
#SELECT
#  direction,
#  from_address,
#  human_readable AS readable,
#  entity_type,
#  amount_display,
#  timestamp_display,
#  to_address
#FROM fund_flow 
#WHERE entity_type = 'Grants Committee'
#AND timestamp_display > '2021-10-07'::DATE  
#AND timestamp_display < '2022-01-08'::DATE
#AND direction = 'Out'
#--where timestamp_display > '2021-10-01T09:26:59'::TIMESTAMP 
#ORDER BY timestamp_display DESC
#)

#SELECT
#  g.direction,
#  g.from_address,
#  g.readable,
#  g.entity_type,
#  g.amount_display,
#  g.timestamp_display,
#  g.to_address,
#  b.human_readable 
#FROM gcs1 g 
#LEFT JOIN bankless_wallet_entity_2 b ON lower(g.to_address) = lower(b.wallet_address)
```

Visualization

```{r, echo=FALSE}
library(tidyverse)
library(scales)

# load data
gcs1 <- read_csv("./sankey/raw_data/s1_fund_flow_gc_2_20220112T062448.csv")
gcs2 <- read_csv("./sankey/raw_data/s2_fund_flow_gc_2_20220112T063018.csv")

# transform
gcs1a <- gcs1 %>%
    mutate(
        season = 1,
        human_readable = if_else(is.na(human_readable), "Misc", human_readable)
    ) %>% 
    select(human_readable, amount_display, season)



gcs2a <- gcs2 %>%
    mutate(
        season = 2,
        human_readable = if_else(is.na(human_readable), "Misc", human_readable)
    ) %>% 
    select(human_readable, amount_display, season)

grants <- rbind(gcs1a, gcs2a)

# scientific notation
options(scipen=999)

# visualize
grants %>%
    mutate(
        season = as.factor(season)
    ) %>%
    group_by(human_readable, season) %>%
    summarise(amount = sum(amount_display)) %>%
    ggplot(aes(x = reorder(human_readable, amount), y = amount, fill = season)) +
    geom_bar(stat = "identity", position = "stack") +
    scale_y_continuous(labels = comma) +
    coord_flip() +
    theme_minimal()
```

## Bankless Vault Fund Distribution (+ Grants Committee)

**Data Source**: 

- Pipeline: Need to update the pipeline to the BANK subgraph in repo: analytics > graphql > exploratory > see `bank_sched.py` or `mck_bank_subgraph5.py`.

- Bankless_wallet_entity: Need to consult this [sheet](https://docs.google.com/spreadsheets/d/1a6ZMclYkESWNwV7xNhT-LELwHtK28wo9f4xx-JGab5k/edit#gid=0) to add additional project, guild multisig & address to `bankless_wallet_entity_2` table in DAODash.

- Postgres DB tables: `stg_subgraph_bank_1` and `bankless_wallet_entity_2`
- Saved Queries: `Fund_Flow_Bankless_Vault` and `Fund_Flow_GC_2`. 

- Raw data: 4 data sets needed to create `full_grants` which is used in the side-by-side bar chart and subsequent sankeys:

gcs1a: `s1_fund_flow_gc_2_20220112T062448`  (see previous step: Grants Committee)
gcs2a: `s2_fund_flow_gc_2_20220112T063018`  (see previous step: Grants Committee)
bv_s1a: `s1_fund_flow_bankless_vault_20220113T082455` 
bv_s2a: `s2_fund_flow_bankless_vault_20220113T082831`



**Procedure Summary**: Borrowing a portion of RTJ's query to create a limited sankey showing the flow from Grants Committee (and Bankless Vault address `0xf26d1bb347a59f6c283c53156519cc1b1abaca51`) into various guilds, projects and initiatives. 

**Outstanding Question**: Why is direction 'in' for `Bankless Vault` (in **Fund_Flow_Bankless_Vault**), but 'out' for `Grants Committee` (in **Fund_Flow_GC_2**)?

**Description of Finding**: Because In Season 1, Analytics Guild received funds from the Grants Committee address, in Season 2, the Analytics Guild received funds from the Bankless Vault address (`0xf26d1bb347a59f6c283c53156519cc1b1abaca51`), we need to combine two CSV datasets to see full picture of Season 1 vs Season 2 comparison.

See DaoDash: `Fund_Flow_Bankless_Vault` (nearly identical to `Fund_Flow_GC_2`, except direction is 'In'). 

```{r, echo=FALSE}
library(tidyverse)
library(scales)

# load data
bv_s1 <- read_csv("./sankey/raw_data/s1_fund_flow_bankless_vault_20220113T082455.csv")
bv_s2 <- read_csv("./sankey/raw_data/s2_fund_flow_bankless_vault_20220113T082831.csv")

# transform
bv_s1a <- bv_s1 %>%
    mutate(
        season = 1
    ) %>%
    select(human_readable, amount_display, season)


bv_s2a <- bv_s2 %>%
    mutate(
        season = 2
    ) %>%
    select(human_readable, amount_display, season)


bv_grants <- rbind(bv_s1a, bv_s2a)

# scientific notation
options(scipen=999)

# visualize
bv_grants %>%
    mutate(
        season = as.factor(season)
    ) %>%
    group_by(human_readable, season) %>%
    summarise(amount = sum(amount_display)) %>%
    ggplot(aes(x = reorder(human_readable, amount), y = amount, fill = season)) +
    geom_bar(stat = "identity", position = "stack") +
    scale_y_continuous(labels = comma) +
    coord_flip() +
    theme_minimal()

# full grants - minus grants committee
full_grants <- rbind(gcs1a, gcs2a, bv_s1a, bv_s2a)

full_grants %>%
    mutate(
        season = as.factor(season)
    ) %>%
    group_by(human_readable, season) %>%
    summarise(amount = sum(amount_display)) %>%
    filter(human_readable != 'Grants Committee') %>%
    ggplot(aes(x = reorder(human_readable, amount), y = amount, fill = season)) +
    geom_bar(stat = "identity", position = "dodge") +
    scale_y_continuous(labels = comma) +
    coord_flip() +
    theme(
        legend.background = element_rect(fill = "#65737e"),
        legend.text = element_text(color = "white"),
        legend.title = element_text(color = "white"),
        panel.background = element_rect(fill = "#65737e"),
        panel.grid.major = element_line(color = "#65737e"),
        panel.grid.minor = element_line(color = "#65737e"),
        plot.background = element_rect(fill = "#65737e"),
        axis.text.x = element_text(color = "white"),
        axis.text.y = element_text(color = "white"),
        axis.title.x = element_text(color = "white"),
        axis.title.y = element_text(color = "white"),
        title = element_text(color = "white", face = "bold")
    ) +
    scale_fill_manual(values = c("black", "red")) +
    labs(
        title = "Funding from Grants Committee | Bankless Vault",
        subtitle = "S1 and S2",
        x = "Projects & Guilds",
        y = "Amount ($BANK)",
        caption = "Powered by DAO Dash"
    )

# coord flip
full_grants %>%
    mutate(
        season = as.factor(season)
    ) %>%
    group_by(human_readable, season) %>%
    summarise(amount = sum(amount_display)) %>%
    filter(human_readable != 'Grants Committee') %>%
    ggplot(aes(x = reorder(human_readable, amount), y = amount, fill = season)) +
    geom_bar(stat = "identity", position = "dodge") +
    scale_y_continuous(labels = comma) +
    theme(
        legend.background = element_rect(fill = "#65737e"),
        legend.text = element_text(color = "white"),
        legend.title = element_text(color = "white"),
        panel.background = element_rect(fill = "#65737e"),
        panel.grid.major = element_line(color = "#65737e"),
        panel.grid.minor = element_line(color = "#65737e"),
        plot.background = element_rect(fill = "#65737e"),
        axis.text.x = element_text(color = "white", angle = 40, hjust = 1, size = 12),
        axis.text.y = element_text(color = "white", size = 12),
        axis.title.x = element_text(color = "white"),
        axis.title.y = element_text(color = "white"),
        title = element_text(color = "white")
    ) +
    scale_fill_manual(values = c("white", "red")) +
    labs(
        title = "Funding from Grants Committee | Bankless Vault",
        subtitle = "S1 and S2",
        x = "Projects & Guilds",
        y = "Amount ($BANK)",
        caption = "visual: @paulapivat | Powered by: DAODash"
    )




```

## Example Sankey

```{r, echo=FALSE}
library(tidyverse)
library(networkD3)

# sample sankey ----

# flow
links <- data.frame(
    source=c("group_A","group_A", "group_B", "group_C", "group_C", "group_E"), 
    target=c("group_C","group_D", "group_E", "group_F", "group_G", "group_H"), 
    value=c(2,3, 2, 3, 1, 3)
)

# nodes
nodes <- data.frame(
    name=c(as.character(links$source), 
           as.character(links$target)) %>% unique()
)

# With networkD3, connection must be provided using id, not using real name like in the links dataframe.. So we need to reformat it.
links$IDsource <- match(links$source, nodes$name)-1 
links$IDtarget <- match(links$target, nodes$name)-1

# Make the Network
p <- sankeyNetwork(Links = links, Nodes = nodes,
              Source = "IDsource", Target = "IDtarget",
              Value = "value", NodeID = "name", 
              sinksRight=FALSE)
p

```



## REVISED Sankey: Grants Committee Vault, Season 1

**Data Source**: See above with Bankless Vault Fund Distribution (+ Grants Committee) data sources.

**Procedure Summary**: Use `full_grants` data frame to create sankey for Season 1 and Season 2.

NOTE: full_grants <- rbind(gcs1a, gcs2a, bv_s1a, bv_s2a). See previous section.
- full_grants combines grants committee + bankless_vault, across s1 and s2
- start with full_grants 

**Description of Finding**: 
- 26 projects/guilds in Season 1
- 33 projects/guilds in Season 2

customize colors and see "pink nodes" for new projects in Season 2. 

```{r, echo=FALSE}
# REVISED Sankey with New Data ----
library(tidyverse)
library(networkD3)

# create id for each node
# Alternative way to replace NA values - this works

# Starting point 'full_grants'
my_links_1 <- full_grants %>%
    filter(season == 1) %>%
    filter(human_readable != 'Grants Committee') %>%
    mutate(
        source = 'Grants Committee Vault'
    ) %>%
    rename(
        target = human_readable,
        value = amount_display
    ) %>%
    select(source, target, value) 


# unique nodes
# find unique values in column
# change 'target' to 'name'
unique_nodes <- unique(my_links_1[c("target")]) %>%
    rename(
        name = target
    ) %>%
    print(n = 100)




# manually create nodes
# NOTE: 'Grants Committee Vault' is first row
my_nodes_1 <- data.frame(name = c(
    "Grants Committee Vault",
     "Analytics Guild", 
     "A/V Guild", 
     "Bankless Academy", 
     "Bankless Loans",  
     "Bankless Website Multisig", 
     "Balancer Multisig", 
     "BED Index",  
     "BizDev Guild", 
     "BountyBoard",                
     "Crypto Sapiens",   
     "DAO Punks", 
     "Degen",  
     "Design Guild",  
     "DevOps Infrastructure Multisig",
     "Devs Guild Multisig", 
     "Education Guild Multisig",  
     "First Quest",
     "Legal Guild",
     "Liquity Project Multisig", 
      "Marketing Guild", 
      "Ops Guild",
     "Research Guild", 
     "S1 Coordinape",
     "Translators Guild",             
     "Treasury Guild",
     "Writers Guild",
     "Misc"  
))


# create id for each node ----
# links$IDsource <- match(links$source, nodes$name)-1 
# links$IDtarget <- match(links$target, nodes$name)-1

my_links_1$IDsource <- match(my_links_1$source, my_nodes_1$name)-1
my_links_1$IDtarget <- match(my_links_1$target, my_nodes_1$name)-1

# add color

my_color_1 <- 'd3.scaleOrdinal() .domain([
                            "Grants Committee Vault",
                            "Analytics Guild", 
                            "A/V Guild", 
                            "Bankless Academy", 
                            "Bankless Loans",  
                            "Bankless Website Multisig", 
                            "Balancer Multisig", 
                            "BED Index",  
                            "BizDev Guild", 
                            "BountyBoard",                
                            "Crypto Sapiens",   
                            "DAO Punks", 
                            "Degen",  
                            "Design Guild",  
                            "DevOps Infrastructure Multisig",
                            "Devs Guild Multisig", 
                            "Education Guild Multisig",  
                            "First Quest",
                            "Legal Guild",
                            "Liquity Project Multisig", 
                            "Marketing Guild", 
                            "Ops Guild",
                            "Research Guild", 
                            "S1 Coordinape",
                            "Translators Guild",             
                            "Treasury Guild",
                            "Writers Guild",                 
                            "Misc"]) .range(["red", 
                                             "#65737e", 
                                             "#65737e", 
                                             "#65737e", 
                                             "#65737e", 
                                             "#65737e",
                                             "#65737e", 
                                             "#65737e", 
                                             "#65737e", 
                                             "#65737e", 
                                             "#65737e", 
                                             "#65737e",
                                             "#65737e", 
                                             "#65737e",
                                             "#65737e", 
                                             "#65737e", 
                                             "#65737e", 
                                             "#65737e", 
                                             "#65737e",
                                             "#65737e", 
                                             "#65737e", 
                                             "#65737e", 
                                             "#65737e", 
                                             "#65737e", 
                                             "#65737e",
                                             "#65737e", 
                                             "#65737e",
                                             "#65737e"
                                    ])'

# sankey
sankeyNetwork(Links = my_links_1, Nodes = my_nodes_1,
              Source = "IDsource", Target = "IDtarget",
              Value = "value", NodeID = "name", colourScale = my_color_1, 
              fontSize = 15, fontFamily = "Helvetica", sinksRight=FALSE)





```

## REVISED Sankey: Grants Committee Vault, Season 2

**Data Source**: 

**Procedure Summary**:

**Description of Finding**s: 

```{r, echo=FALSE}

# REVISED Sankey with New Data ----
library(tidyverse)
library(networkD3)

# create id for each node
# Alternative way to replace NA values - this works

# Starting point 'full_grants'
my_links_2 <- full_grants %>%
    filter(season == 2) %>%
    filter(human_readable != 'Grants Committee') %>%
    mutate(
        source = 'Grants Committee Vault'
    ) %>%
    rename(
        target = human_readable,
        value = amount_display
    ) %>%
    select(source, target, value) 

# unique nodes
# find unique values in column
# change 'target' to 'name'
unique_nodes_2 <- unique(my_links_2[c("target")]) %>%
    rename(
        name = target
    ) %>%
    print(n = 100)

# MANUALLY create nodes
# NOTE: 'Grants Committee Vault' is first row
my_nodes_2 <- data.frame(name = c(
    "Grants Committee Vault",
    "Analytics Guild",
    "A/V Guild",
    "Bankless Academy",	
    "Bankless Loans",
    "Bankless Website Multisig",
    "BED Index",
    "BizDev Guild",	
    "BountyBoard",				
    "DAO Punks",
    "Degen",
    "Design Guild",	
    "DevOps Infrastructure Multisig",
    "Devs Guild Multisig",
    "Education Guild Multisig",	
    "First Quest",
    "Legal Guild",
    "Liquity Project Multisig",
    "Marketing Guild",
    "Ops Guild",
    "Research Guild",
    "S1 Coordinape",
    "Translators Guild",
    "Treasury Guild",
    "Writers Guild",
    "Balancer Liquidity Mining Program Multisig",
    "Book Club Multisig",
    "Content Gateway",
    "DaoDash",				
    "FightClub",				
    "Flipper Zone Multisig",
    "International Media Node Multisig",
    "NewsletterTeam",				
    "Podcast Hatchery Multisig",				
    "Misc"
))

# create id for each node ----
# links$IDsource <- match(links$source, nodes$name)-1 
# links$IDtarget <- match(links$target, nodes$name)-1

my_links_2$IDsource <- match(my_links_2$source, my_nodes_2$name)-1
my_links_2$IDtarget <- match(my_links_2$target, my_nodes_2$name)-1


# add color

my_color_2 <- 'd3.scaleOrdinal() .domain([
                            "Grants Committee Vault",
                            "Analytics Guild",
                            "A/V Guild",
                            "Bankless Academy",	
                            "Bankless Loans",
                            "Bankless Website Multisig",
                            "BED Index",
                            "BizDev Guild",	
                            "BountyBoard",				
                            "DAO Punks",
                            "Degen",
                            "Design Guild",	
                            "DevOps Infrastructure Multisig",
                            "Devs Guild Multisig",
                            "Education Guild Multisig",	
                            "First Quest",
                            "Legal Guild",
                            "Liquity Project Multisig",
                            "Marketing Guild",
                            "Ops Guild",
                            "Research Guild",
                            "S1 Coordinape",
                            "Translators Guild",
                            "Treasury Guild",
                            "Writers Guild",
                            "Balancer Liquidity Mining Program Multisig",
                            "Book Club Multisig",
                            "Content Gateway",
                            "DaoDash",				
                            "FightClub",				
                            "Flipper Zone Multisig",
                            "International Media Node Multisig",
                            "NewsletterTeam",				
                            "Podcast Hatchery Multisig",				
                            "Misc"]) .range(["red", 
                                             "#65737e", 
                                             "#65737e", 
                                             "#65737e", 
                                             "#65737e", 
                                             "#65737e",
                                             "#65737e", 
                                             "#65737e", 
                                             "#65737e", 
                                             "#65737e", 
                                             "#65737e", 
                                             "#65737e",
                                             "#65737e", 
                                             "#65737e",
                                             "#65737e", 
                                             "#65737e", 
                                             "#65737e", 
                                             "#65737e", 
                                             "#65737e",
                                             "#65737e", 
                                             "#65737e", 
                                             "#ff9999", 
                                             "#ff9999", 
                                             "#ff9999", 
                                             "#ff9999",
                                             "#ff9999", 
                                             "#ff9999",
                                             "#ff9999",
                                             "#ff9999",
                                             "#ff9999", 
                                             "#ff9999", 
                                             "#ff9999", 
                                             "#ff9999", 
                                             "#ff9999", 
                                             "#ff9999",
                                    ])'


# sankey
sankeyNetwork(Links = my_links_2, Nodes = my_nodes_2,
              Source = "IDsource", Target = "IDtarget",
              Value = "value", NodeID = "name", colourScale = my_color_2, 
              fontSize = 15, fontFamily = "Helvetica", sinksRight=FALSE)

```


## Bounty Board

**Data Source**: Bounty Board team production database in Mongo. Because I was doing summary statistics comparing Season 1 and Season 2. I queried the database for metrics at a point in a time like so:

**Query Database**: query from database in prod. WIP. 

Number of bounties:                 S1: 40, S2: 66+

Value committed to bounties:        S1: 68K, S2: 209K

Update: 15/01/22 for numbers

Then I manually created a dataframe.

**Procedure Summary**:

**Description of Finding**: Number of Bounties and 

**Task**: Query total number of bounties and total value committed to bounties between S1 v S2.



```{r, echo=FALSE}

season <- c('1','2')
num_bounties <- c(40, 69)
value_in_bounties <- c(68071, 215506)


bb_df <- data.frame(season, num_bounties, value_in_bounties)


# geom_text(aes(label = count), position = position_stack(vjust = 1.5), color = "white")

# number of bounties: s1 vs s2
bb_df %>%
    ggplot(aes(x = season, y = num_bounties, fill = season)) +
    geom_col() +
    geom_text(aes(label = num_bounties), vjust = 1.3, color = "white", size = 15) +
    scale_fill_manual(values = c("black", "red")) +
    theme(
        legend.position = "none",
        panel.background = element_rect(fill = "#798f9b"),
        panel.grid.major = element_line(color = "#798f9b"),
        panel.grid.minor = element_line(color = "#798f9b"),
        plot.background = element_rect(fill = "#798f9b"),
        axis.text.x = element_text(color = "white", size = 15),
        axis.text.y = element_text(color = "white", size = 15),
        axis.title.x = element_text(color = "white"),
        axis.title.y = element_text(color = "white"),
        title = element_text(color = "white", size = 16)
    ) +
    labs(
        title = "Number of Bounties Posted",
        subtitle = "Season 1 vs Season 2",
        y = "Number of Bounties",
        x = "Season",
        caption = "data: BanklessDAO Bounty Board | visual: @paulapivat"
    )

# value in bounties: s1 vs s2
bb_df %>%
    ggplot(aes(x = season, y = value_in_bounties, fill = season)) +
    geom_col() +
    geom_text(aes(label = scales::comma(value_in_bounties)), vjust = 1.3, color = "white", size = 12) +
    scale_fill_manual(values = c("black", "red")) +
    scale_y_continuous(labels = comma) +
    theme(
        legend.position = "none",
        panel.background = element_rect(fill = "#798f9b"),
        panel.grid.major = element_line(color = "#798f9b"),
        panel.grid.minor = element_line(color = "#798f9b"),
        plot.background = element_rect(fill = "#798f9b"),
        axis.text.x = element_text(color = "white", size = 15),
        axis.text.y = element_text(color = "white", size = 15),
        axis.title.x = element_text(color = "white"),
        axis.title.y = element_text(color = "white"),
        title = element_text(color = "white", size = 16)
    ) +
    labs(
        title = "Total Value Committed to Bounties",
        subtitle = "Season 1 vs Season 2",
        y = "Value Committed (BANK)",
        x = "Season",
        caption = "data: BanklessDAO Bounty Board | visual: @paulapivat"
    )





```


## Coordinape Distribution

**Data Source**: 
- Pipeline: see `data_request.py` and `coordinape_rounds.py` in repo: analytics > coordinape
- DAODash table: `coordinape_rounds_3`
- DaoDash query, `Seasonal Coordinape Distribution`
- Raw data: see s3_data_activity > coordinape > raw_data > s1_coordinape_distribution and s2_coordinape_distribution.

**Procedure Summary**: Query from DAO Dash, save 2 CSV files. Run data transformations in R, but ultimately manually create dataframe with important summary data.

**Description of Finding**: Query comparison of tokens/bank distributed via Coordinape in S1 vs S2. Coordinape tokens, givers and receivers are all up.


```{r, echo=FALSE}
library(tidyverse)

coord_s1 <- read_csv("./coordinape/raw_data/s1_coordinape_distribution_20220112T121445.csv")
coord_s2 <- read_csv("./coordinape/raw_data/s2_coordinape_distribution_20220112T120953.csv")

# sum tokens distributed - Season 1: 192,076 , Season 2: 425,561
coord_s1 %>%
    summarise(sum_tokens = sum(tokens))

coord_s2 %>%
    summarise(sum_tokens = sum(tokens))

# how many senders, Season 1: n = 302, Season 2: 458
coord_s1 %>%
    group_by(sender_id) %>%
    tally(sort = TRUE)

coord_s1 %>%
    distinct(sender_id) %>%
    count()

coord_s2 %>%
    distinct(sender_id) %>%
    count()

# how many recipients, Season 1: n = 416, Season 2: n = 481
coord_s1 %>%
    distinct(recipient_id) %>%
    count()

coord_s2 %>%
    distinct(recipient_id) %>%
    count()


# create dataframes for Tokens distributed, Number of Senders and Number of Receivers 
season <- c("1", "2")
tokens_distributed <- c(192076, 425561)
num_senders <- c(302, 458)
num_receivers <- c(416, 481)

coord_df <- data.frame(season, tokens_distributed, num_senders, num_receivers)

# scientific notation
options(scipen=999)



# visualize tokens_distributed
coord_df %>%
    ggplot(aes(x = season, y = tokens_distributed, fill = season)) +
    geom_col() +
    geom_text(aes(label = scales::comma(tokens_distributed)), vjust = 1.3, color = "white", size = 12) +
    scale_fill_manual(values = c("black", "red")) +
    scale_y_continuous(labels = comma) +
    theme(
        legend.position = "none",
        panel.background = element_rect(fill = "#798f9b"),
        panel.grid.major = element_line(color = "#798f9b"),
        panel.grid.minor = element_line(color = "#798f9b"),
        plot.background = element_rect(fill = "#798f9b"),
        axis.text.x = element_text(color = "white", size = 15),
        axis.text.y = element_text(color = "white", size = 15),
        axis.title.x = element_text(color = "white"),
        axis.title.y = element_text(color = "white"),
        title = element_text(color = "white", size = 16)
    ) +
    labs(
        title = "Coordinape: Tokens Distributed",
        subtitle = "Season 1 vs Season 2",
        y = "Tokens Distributed",
        x = "Season",
        caption = "visual: @paulapivat | Powered by: DAODash"
    )

# visualize num_senders
coord_df %>%
    ggplot(aes(x = season, y = num_senders, fill = season)) +
    geom_col() +
    geom_text(aes(label = scales::comma(num_senders)), vjust = 1.3, color = "white", size = 12) +
    scale_fill_manual(values = c("black", "red")) +
    scale_y_continuous(labels = comma) +
    theme(
        legend.position = "none",
        panel.background = element_rect(fill = "#798f9b"),
        panel.grid.major = element_line(color = "#798f9b"),
        panel.grid.minor = element_line(color = "#798f9b"),
        plot.background = element_rect(fill = "#798f9b"),
        axis.text.x = element_text(color = "white", size = 15),
        axis.text.y = element_text(color = "white", size = 15),
        axis.title.x = element_text(color = "white"),
        axis.title.y = element_text(color = "white"),
        title = element_text(color = "white", size = 16)
    ) +
    labs(
        title = "Coordinape: Number of Senders",
        subtitle = "Season 1 vs Season 2",
        y = "Number of Senders",
        x = "Season",
        caption = "visual: @paulapivat | Powered by: DAODash"
    )

# visualize num_receivers
coord_df %>%
    ggplot(aes(x = season, y = num_receivers, fill = season)) +
    geom_col() +
    geom_text(aes(label = scales::comma(num_receivers)), vjust = 1.3, color = "white", size = 12) +
    scale_fill_manual(values = c("black", "red")) +
    scale_y_continuous(labels = comma) +
    theme(
        legend.position = "none",
        panel.background = element_rect(fill = "#798f9b"),
        panel.grid.major = element_line(color = "#798f9b"),
        panel.grid.minor = element_line(color = "#798f9b"),
        plot.background = element_rect(fill = "#798f9b"),
        axis.text.x = element_text(color = "white", size = 15),
        axis.text.y = element_text(color = "white", size = 15),
        axis.title.x = element_text(color = "white"),
        axis.title.y = element_text(color = "white"),
        title = element_text(color = "white", size = 16)
    ) +
    labs(
        title = "Coordinape: Number of Receivers",
        subtitle = "Season 1 vs Season 2",
        y = "Number of Receivers",
        x = "Season",
        caption = "visual: @paulapivat | Powered by: DAODash"
    )





```


## Tips Given & Received

**Data Source**: 

- Pipeline: McKethanor built this pipeline to our postgres db. 
- DaoDash table: `tipping` has most up-to-date info. 
- DaoDash saved query: `Seasonal Tip Distribution` 

Season 1 Tip Distribution (2873 rows, 983,019 tips given), WHERE timestamp < '2021-10-08'::DATE AND timestamp > '2021-06-14'::DATE 

Season 2 Tip Distribution (1336 rows, 337,173 tips given), WHERE timestamp > '2021-10-07'::DATE AND timestamp < '2022-01-08'::DATE 

**Procedure Summary**: Get comparison between S1 and S2, create tibble/dataframe to display data. Ultimately create own dataframe.  

**Description of Finding**: Tipping has dropped by -66%



```{r, echo=FALSE}
tips_df <- data.frame(season = c("1", "2"), tips_distributed = c(983019, 337173))

tips_df %>%
    ggplot(aes(x = season, y = tips_distributed, fill = season)) +
    geom_col() +
    geom_text(aes(label = scales::comma(tips_distributed)), vjust = 1.3, color = "white", size = 12) +
    scale_fill_manual(values = c("black", "red")) +
    scale_y_continuous(labels = comma) +
    theme(
        legend.position = "none",
        panel.background = element_rect(fill = "#798f9b"),
        panel.grid.major = element_line(color = "#798f9b"),
        panel.grid.minor = element_line(color = "#798f9b"),
        plot.background = element_rect(fill = "#798f9b"),
        axis.text.x = element_text(color = "white", size = 15),
        axis.text.y = element_text(color = "white", size = 15),
        axis.title.x = element_text(color = "white"),
        axis.title.y = element_text(color = "white"),
        title = element_text(color = "white", size = 16)
    ) +
    labs(
        title = "Total Tips Distributed",
        subtitle = "Season 1 vs Season 2",
        y = "Tips Distributed",
        x = "Season",
        caption = "visual: @paulapivat | Powered by: DAODash"
    )





```




## Number of Bank Holders (Membership Categories); S1 vs S2

**Data Source**: Due to inconsistency between queries in Dune Analytics, DAO Dash and even Google Biq Query, more time needs to be spent to reconcile differences between seemingly identical queries. 

In the short-term, use Dune Analytics. 

**Procedure Summary**:

**Description of Finding**s: 

**Task**: Compare S1 vs S2 on all membership categories.

See `mem_1_10K_bank_holdings_time_range` and other segments downloaded in raw csv. 
Data gathered from DAODash table.

See also: 
- BANK Holders 10 - 35K
- BANK Holders 35 - 150K
- BANK Holders 150K - 1.5M

```{r, echo=FALSE}
library(tidyverse)
library(lubridate)
library(zoo)

bank_sg <- read_csv("./bank_subgraph/raw_data/mem_1_10K_bank_holdings_time_range_20220102T062946.csv")

# turn time stamp into date
bank_sg %>%
    mutate(
        new_day = date(day)
    ) %>%
    group_by(new_day) %>%
    tally(sort = TRUE) %>%
    arrange(new_day) %>%
    mutate(
        cummulative = cumsum(n),
        change = n - lag(n,1,default = 0.0),
        series = cummulative + change
    )%>%
    ggplot(aes(x = new_day, y = series)) +
    geom_line() +
    scale_x_date(date_breaks = "1 month") +
    labs(
        title = "Number of BANK Holders overtime",
        subtitle = "1 - 10K BANK"
    )

?rollsum
```








## Discourse

**Data Source**: 

**Procedure Summary**:

**Description of Finding**s: 

Task: Connect to API to query forum posts with polls and number of people voting.

Challenge: API documentation does not mention Polls or Votes. See [documentation](https://docs.discourse.org/) here. 

Progress: Established API connection with the `pydiscourse` https://github.com/BanklessDAO/analytics/blob/main/discourse_forum/api_connection.py

Ended up downloading CSV manually of all users, instead of votes, will track other engagement metrics like: 
- topics_entered
- posts_read_count
- time_read
- topic_count

*note*: remove email column, then save raw data to github

```{r, echo=FALSE}

```


## First Quest

Task: Query number of new members going through First Quest 

**Challenge**: Data inserted at 2021-11-18, might have insufficient data to make S1 vs S2 comparison. 

Just show S2 First Quest data standalone (compare Funnel shape from two time periods).

```{r, echo=FALSE}

```




## Next Section

```{r, echo=FALSE}

```


## Next Section

```{r, echo=FALSE}

```


